---
title: "Experiment 1.5 Analysis"
author: "Sanne Poelstra"
date: "14/03/2021"
output: html_document
---

```{r, include = FALSE}
rm(list=ls())
library(plotfunctions)
library("plotrix")
library("phonTools")
```

```{r, reading in the csv file}
d <- read.csv("Experiment1_5.csv", header = TRUE, sep = ',')
#This is quite a lot so I want to trim it somewhat, e.g. things such as font are not needed
dat <- d[, c("A", "A1", "A1_alt", "A2", "A3", "A3_alt", "B", "B1", "B1_alt", "B2", "B3", "B3_alt", "X", "X1", "X1_alt", "X2", "X3", "X3_alt", "C", "C_alt", "Outcome", "Stim1", "Stim2", "responseR1", "responseR2", "responseR3",  "block1", "block2", "block3", "average_response_time", "avg_rt", "NewAnswers", "Practice", "date_starttime", "jatosStudyResultId", "pos1X", "pos1Y", "pos2X", "pos2Y", "prolific_id", "response_time", "Cond", "Train_Test", "screen_availableHeight", "screen_availableWidth",  "timeout_occurred", "total_response_time", "Trial")]

head(dat)

#now there were also some prolific IDs that were rejected, so I have to remove them
dat <- dat[which(dat$prolific_id != "5c055cbe4692a7000166a1f5" & dat$prolific_id != "602a79ad86b0770624288e16" & dat$prolific_id != "5f3ab64e0dda76127bcc344e" & dat$prolific_id != "5fe150610a5e7fbea05b7c92" & dat$prolific_id != "5db8b0df497a6e000afdf49a" & dat$prolific_id != "5f2b24c4224df7527baee383" & dat$prolific_id != "5f6b36e1ab9578230dd425df"),]
#5f6b36e1ab9578230dd425df is me

table(unique(dat$prolific_id)) #10 participants!
```
```{r, warning = FALSE}
#As we don't know yet which condition was the first block, I'm going to have to assign a new column with that value
#blockNr depends on the value of block 1. If block 1 was 0 (internally 0 meant condition 0) and the condition of this current trial is 0, then we give this the value "block 1"

dat$blockNr <- ""
dat <- within(dat, blockNr[block1 == '0' & Cond == 0] <- 'Block1')
dat <- within(dat, blockNr[block1 == '1' & Cond == 50] <- 'Block1')
dat <- within(dat, blockNr[block1 == '2' & Cond == 100] <- 'Block1')
dat <- within(dat, blockNr[block2 == '0' & Cond == 0] <- 'Block2')
dat <- within(dat, blockNr[block2 == '1' & Cond == 50] <- 'Block2')
dat <- within(dat, blockNr[block2 == '2' & Cond == 100] <- 'Block2')
dat <- within(dat, blockNr[block3 == '0' & Cond == 0] <- 'Block3')
dat <- within(dat, blockNr[block3 == '1' & Cond == 50] <- 'Block3')
dat <- within(dat, blockNr[block3 == '2' & Cond == 100] <- 'Block3')

dat$CondFirstBlock <- ''
dat$CondSecondBlock <- ''
dat$CondThirdBlock <- '' 

#dat$prolific_id <- as.factor(dat$prolific_id)

#to later compare the cues in the test phase to the condition they were originally asked in, we need another new column
#so for each participant, what condition was block 1? Save that in a row, what condition was block 3?
for(i in unique(dat$prolific_id)){
  dat <- within(dat, CondFirstBlock[prolific_id == i] <- Cond[prolific_id == i & blockNr == "Block1"])
  dat <- within(dat, CondSecondBlock[prolific_id == i] <- Cond[prolific_id == i & blockNr == "Block2"])
  dat <- within(dat, CondThirdBlock[prolific_id == i] <- Cond[prolific_id == i & blockNr == "Block3"])
} #HAAKJES
```


```{r, collect the data for the graphs}
#averages per condition, for X A and B
#responseR1 is always A, R2 is always B and R3 is always X

#train is the training phase. I want to make both a plot with 1's as answers removed, and one with all the answers, so I'll create two "train" dataframes
train1 <- dat[which(dat$Train_Test == "Train"),]
train <- dat[which(dat$Train_Test == "Train"),]

#Filter the 999 ones
train$responseR1[train$responseR1 == 999] <- NA
train$responseR2[train$responseR2 == 999] <- NA
train$responseR3[train$responseR3 == 999] <- NA

train1$responseR1[train1$responseR1 == 999] <- NA
train1$responseR2[train1$responseR2 == 999] <- NA
train1$responseR3[train1$responseR3 == 999] <- NA

train1$responseR1[train$responseR1 == 1] <- NA
train1$responseR2[train$responseR2 == 1] <- NA
train1$responseR3[train$responseR3 == 1] <- NA

train$Cond <- as.factor(train$Cond)
train$Cond <- factor(train$Cond, levels = c("0", "50", "100"))

train1$Cond <- as.factor(train1$Cond)
train1$Cond <- factor(train1$Cond, levels = c("0", "50", "100"))

a <- aggregate(list(train$responseR1, train$responseR2, train$responseR3), list(train$Cond), mean, na.rm = T)
b <- aggregate(list(train1$responseR1, train1$responseR2, train1$responseR3), list(train1$Cond), mean, na.rm = T)

colnames(a) <- c("Cond", "A", "B", "X")
colnames(b) <- c("Cond", "A", "B", "X")
head(a)
head(b)

SECondA <- c(std.error(train$responseR1[train$Cond == "0"]), std.error(train$responseR1[train$Cond == "50"]), std.error(train$responseR1[train$Cond == "100"]))
SECondB <- c(std.error(train$responseR2[train$Cond == "0"]), std.error(train$responseR2[train$Cond == "50"]), std.error(train$responseR2[train$Cond == "100"]))
SECondX <- c(std.error(train$responseR3[train$Cond == "0"]), std.error(train$responseR3[train$Cond == "50"]), std.error(train$responseR3[train$Cond == "100"]))

SECondA
SECondB
SECondX

#se seems fine! Not a lot of individual difference i'd say

```

```{r}
hist(train$responseR1[train$Cond == "100"], breaks = 10, main = "Frequency of each score given to A in the 100-0 Condition", xlab = "Score")
mean(train$responseR1[train$Cond == "100"], na.rm = TRUE)
```
<br/> This histogram shows the condition where A (responseR1) always leads to a diamond outcome. Just as with the full experiment, there are quite a lot of 1's here, that you would not expect.


```{r}
hist(train$responseR2[train$Cond == "100"], breaks = 10, main = "Frequency of each score given to B in the 100-0 Condition", xlab = "Score")
mean(train$responseR2[train$Cond == "100"], na.rm = TRUE)

```
<br/> This histogram shows the condition where B (responseR2) never leads to a diamond outcome. Here the amount of 1's make more sense, and I'm glad to see that at least in comparison they differ?

```{r}
par(mfrow = c(2,2))
hist(train$responseR1[train$Cond == "0"], breaks = 10, main = "Frequency of each score given to\n A in the 50-50 Condition", xlab = "Score", ylim = c(0,80), cex.lab = 1.2, cex.sub = 1.5)
hist(train$responseR2[train$Cond == "0"], breaks = 10, main = "Frequency of each score given to\n B in the 50-50 Condition", xlab = "Score", ylim = c(0,80), cex.lab = 1.2, cex.sub = 1.5)
hist(train$responseR3[train$Cond == "0"], breaks = 10, main = "Frequency of each score given to\n X in the 50-50 Condition", xlab = "Score", ylim = c(0,80), cex.lab = 1.2, cex.sub = 1.5)

par(mfrow = c(2,2))
hist(train$responseR1[train$Cond == "50"], breaks = 10, main = "Frequency of each score given to\n A in the 75-25 Condition", xlab = "Score", ylim = c(0,95), cex.lab = 1.2, cex.sub = 1.5)
hist(train$responseR2[train$Cond == "50"], breaks = 10, main = "Frequency of each score given to\n B in the 75-25 Condition", xlab = "Score", ylim = c(0,95), cex.lab = 1.2, cex.sub = 1.5)
hist(train$responseR3[train$Cond == "50"], breaks = 10, main = "Frequency of each score given to\n X in the 75-25 Condition", xlab = "Score", ylim = c(0,95), cex.lab = 1.2, cex.sub = 1.5)

par(mfrow = c(2,2))
hist(train$responseR1[train$Cond == "100"], breaks = 10, main = "Frequency of each score given to\n A in the 100-0 Condition", xlab = "Score", ylim = c(0,95), cex.lab = 1.2, cex.sub = 1.5)
hist(train$responseR2[train$Cond == "100"], breaks = 10, main = "Frequency of each score given to\n B in the 100-0 Condition", xlab = "Score", ylim = c(0,95), cex.lab = 1.2, cex.sub = 1.5)
hist(train$responseR3[train$Cond == "100"], breaks = 10, main = "Frequency of each score given to\n X in the 100-0 Condition", xlab = "Score", ylim = c(0,95), cex.lab = 1.2, cex.sub = 1.5)
```


```{r}
#As there are lots of 1's let's see how often people scored 1's on average for A B and X (over all conditions)

#Create a subset of data with just the 1's in there
OnesR1 <- subset(train, train$responseR1 == 1)
OnesR2 <- subset(train, train$responseR2 == 1)
OnesR3 <- subset(train, train$responseR3 == 1)
#Take the sum of these ones over participants (as we want to know how often (on average) one participant scored a 1 for A, B or X)
SumOnesR1 <- aggregate(OnesR1$responseR1, list(OnesR1$prolific_id), sum)
SumOnesR2 <- aggregate(OnesR2$responseR2, list(OnesR2$prolific_id), sum)
SumOnesR3 <- aggregate(OnesR3$responseR3, list(OnesR3$prolific_id), sum)
#then take the mean
AvgOnesR1 <- mean(SumOnesR1$x)
AvgOnesR2 <- mean(SumOnesR2$x)
AvgOnesR3 <- mean(SumOnesR3$x)
AvgOnesR1
AvgOnesR2
AvgOnesR3
```
The average amount of 1's given to A is 16, which is 33.3% of all trails, and 4 higher than in the original experiment. <br/>
The average amount of 1's given to B is 23, which is 47,9% of all trials, and is 7 higher than in the original experiment. <br/>
And the average amount of 1's given to X is 6, which is 12.5% of all trials, and is 1 lower than the original experiment. <br/>
You would expect that B is scored lower over all (as it's the least predictive over all), and A to be scored higher over all, so have less 1's than the rest. However what we see here is that X, the stimuli that always appears is actually scored 1 the least amount of times.


```{r}
#over the 16 trials, for each of the conditions, get the average response for A, B and X
AllTrials <- aggregate(list(train$responseR1, train$responseR2, train$responseR3), list(train$Cond, train$Trial), mean, na.rm = T)
AllTrials1 <- aggregate(list(train1$responseR1, train1$responseR2, train1$responseR3), list(train1$Cond, train1$Trial), mean, na.rm = T)
colnames(AllTrials) <- c("Cond", "Trial", "A", "B", "X") 
colnames(AllTrials1) <- c("Cond", "Trial", "A", "B", "X")

#Then split this into the different conditions
Cond000 <- AllTrials[which(AllTrials$Cond==0),]
Cond050 <- AllTrials[which(AllTrials$Cond==50),]
Cond100 <- AllTrials[which(AllTrials$Cond==100),]

#This is then the one without 1's
Cond0001 <- AllTrials1[which(AllTrials1$Cond==0),]
Cond0501 <- AllTrials1[which(AllTrials1$Cond==50),]
Cond1001 <- AllTrials1[which(AllTrials1$Cond==100),]

SETrials000A <- c(std.error(train$responseR1[train$Cond == "0" & train$Trial == '1']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '2']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '3']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '4']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '5']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '6']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '7']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '8']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '9']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '10']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '11']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '12']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '13']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '14']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '15']), std.error(train$responseR1[train$Cond == "0" & train$Trial == '16']))
SETrials000B <- c(std.error(train$responseR2[train$Cond == "0" & train$Trial == '1']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '2']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '3']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '4']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '5']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '6']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '7']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '8']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '9']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '10']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '11']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '12']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '13']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '14']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '15']), std.error(train$responseR2[train$Cond == "0" & train$Trial == '16']))
SETrials000X <- c(std.error(train$responseR3[train$Cond == "0" & train$Trial == '1']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '2']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '3']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '4']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '5']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '6']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '7']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '8']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '9']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '10']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '11']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '12']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '13']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '14']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '15']), std.error(train$responseR3[train$Cond == "0" & train$Trial == '16']))


SETrials050A <- c(std.error(train$responseR1[train$Cond == "50" & train$Trial == '1']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '2']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '3']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '4']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '5']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '6']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '7']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '8']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '9']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '10']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '11']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '12']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '13']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '14']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '15']), std.error(train$responseR1[train$Cond == "50" & train$Trial == '16']))
SETrials050B <- c(std.error(train$responseR2[train$Cond == "50" & train$Trial == '1']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '2']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '3']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '4']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '5']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '6']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '7']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '8']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '9']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '10']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '11']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '12']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '13']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '14']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '15']), std.error(train$responseR2[train$Cond == "50" & train$Trial == '16']))
SETrials050X <- c(std.error(train$responseR3[train$Cond == "50" & train$Trial == '1']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '2']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '3']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '4']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '5']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '6']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '7']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '8']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '9']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '10']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '11']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '12']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '13']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '14']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '15']), std.error(train$responseR3[train$Cond == "50" & train$Trial == '16']))

SETrials100A <- c(std.error(train$responseR1[train$Cond == "100" & train$Trial == '1']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '2']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '3']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '4']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '5']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '6']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '7']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '8']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '9']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '10']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '11']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '12']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '13']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '14']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '15']), std.error(train$responseR1[train$Cond == "100" & train$Trial == '16']))
SETrials100B <- c(std.error(train$responseR2[train$Cond == "100" & train$Trial == '1']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '2']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '3']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '4']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '5']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '6']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '7']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '8']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '9']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '10']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '11']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '12']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '13']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '14']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '15']), std.error(train$responseR2[train$Cond == "100" & train$Trial == '16']))
SETrials100X <- c(std.error(train$responseR3[train$Cond == "100" & train$Trial == '1']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '2']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '3']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '4']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '5']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '6']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '7']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '8']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '9']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '10']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '11']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '12']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '13']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '14']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '15']), std.error(train$responseR3[train$Cond == "100" & train$Trial == '16']))


SETrials000A
SETrials000B
SETrials000X
#A LOT higher (almost double of Exp 1). With def more variation (1! but also 0.6)


SETrials050A
SETrials050B
SETrials050X
#Same here, also when compared to 000


SETrials100A
SETrials100B
SETrials100X
#Same heren


```
Here too, the values in Cond000, Cond050 and Cond100 differ ever so slightly from the averages in a (the one that is used to plot the plot below). This could be due to rounding errors (as here we first aggregate over trial as well instead of just fully over condition). But it's important to note!

### Averages
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(-5,105),c(0,8), xaxt = "none", ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994", xlab = "Condition", ylab = "Causal rating score")
A <- c(4.3,5.7,7.6)
B <- c(2.7, 1.1, 0.2)
X <- c(3.2,3,1.6)
points(c(0, 50, 100),A, pch = 0, type = "b", col = "indianred1")
points(c(0, 50, 100),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0, 50, 100),X, pch =15, type = "b", lty = 4, col = "limegreen")
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
axis(1, at = c(0,50,100), labels = c("50-50", "75-25", "100-0")) 

#Our experiment
emptyPlot(c(-5,105),c(1,9), xaxt = "none", ymark=c(1,2,3,4,5,6,7,8,9), bty='n', main = "Our Experiment 1B", xlab = "Condition", ylab = "Causal rating score")
A <- c(a$A)
B <- c(a$B)
X <- c(a$X)
points(c(0, 50, 100),A, pch = 0, type = "b", col = "indianred1")
points(c(0, 50, 100),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0, 50, 100),X, pch =15, type = "b", lty = 4, col = "limegreen")
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
axis(1, at = c(0,50,100), labels = c("50-50", "75-25", "100-0")) 

#Our experiment with 1's removed
emptyPlot(c(-5,105),c(1,9), xaxt = "none", ymark=c(1,2,3,4,5,6,7,8,9), bty='n', main = "Our Experiment 1B with 1's\n removed", xlab = "Condition", ylab = "Causal rating score")
A <- c(b$A)
B <- c(b$B)
X <- c(b$X)
points(c(0, 50, 100),A, pch = 0, type = "b", col = "indianred1")
points(c(0, 50, 100),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0, 50, 100),X, pch =15, type = "b", lty = 4, col = "limegreen")
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
axis(1, at = c(0,50,100), labels = c("50-50", "75-25", "100-0")) 

```

### Averages Thicker lines
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(-5,105),c(0,8), xaxt = "none", ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994", xlab = "Condition", ylab = "Causal rating score")
A <- c(4.3,5.7,7.6)
B <- c(2.7, 1.1, 0.2)
X <- c(3.2,3,1.6)
points(c(0, 50, 100),A, pch = 0, type = "b", col = "indianred1", lwd = 2)
points(c(0, 50, 100),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd = 2)
points(c(0, 50, 100),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd = 2)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
axis(1, at = c(0,50,100), labels = c("50-50", "75-25", "100-0")) 

#Our experiment
emptyPlot(c(-5,105),c(1,9), xaxt = "none", ymark=c(1,2,3,4,5,6,7,8,9), bty='n', main = "Our Experiment 1B", xlab = "Condition", ylab = "Causal rating score")
A <- c(a$A)
B <- c(a$B)
X <- c(a$X)
points(c(0, 50, 100),A, pch = 0, type = "b", col = "indianred1", lwd =2 )
points(c(0, 50, 100),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd =2)
points(c(0, 50, 100),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd = 2)
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
axis(1, at = c(0,50,100), labels = c("50-50", "75-25", "100-0")) 

#Our experiment with 1's removed
emptyPlot(c(-5,105),c(1,9), xaxt = "none", ymark=c(1,2,3,4,5,6,7,8,9), bty='n', main = "Our Experiment 1B with 1's\n removed", xlab = "Condition", ylab = "Causal rating score")
A <- c(b$A)
B <- c(b$B)
X <- c(b$X)
points(c(0, 50, 100),A, pch = 0, type = "b", col = "indianred1", lwd = 2)
points(c(0, 50, 100),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd =2)
points(c(0, 50, 100),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd =2)
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
axis(1, at = c(0,50,100), labels = c("50-50", "75-25", "100-0")) 

```

### Averages SE
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(-5,105),c(0,8), xaxt = "none", ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994", xlab = "Condition", ylab = "Causal rating score")
A <- c(4.3,5.7,7.6)
B <- c(2.7, 1.1, 0.2)
X <- c(3.2,3,1.6)
points(c(0, 50, 100),A, pch = 0, type = "b", col = "indianred1")
points(c(0, 50, 100),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0, 50, 100),X, pch =15, type = "b", lty = 4, col = "limegreen")
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
axis(1, at = c(0,50,100), labels = c("50-50", "75-25", "100-0")) 

#Our experiment
emptyPlot(c(-5,105),c(1,9), xaxt = "none", ymark=c(1,2,3,4,5,6,7,8,9), bty='n', main = "Our Experiment 1B, with SE", xlab = "Condition", ylab = "Causal rating score")
A <- c(a$A)
B <- c(a$B)
X <- c(a$X)
points(c(0, 50, 100),A, pch = 0, type = "b", col = "indianred1")
points(c(0, 50, 100),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0, 50, 100),X, pch =15, type = "b", lty = 4, col = "limegreen")
errorbars(x= c(0,50,100), y = a$A, top = SECondA, bottom = SECondA, add = TRUE, length = 0.05)
errorbars(x= c(0,50,100), y = a$B, top = SECondB, bottom = SECondB, add = TRUE, length = 0.05)
errorbars(x= c(0,50,100), y = a$X, top = SECondX, bottom = SECondX, add = TRUE, length = 0.05)
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
axis(1, at = c(0,50,100), labels = c("50-50", "75-25", "100-0")) 
```
</br> def bigger SE than in the first experiment

### Cond 000 
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 50-50", xlab = "Trial", ylab = "Causal rating score")
A <- c(4.9, 5, 5.1, 3.2, 2.8, 2.4, 2.2, 4.5, 4, 3, 2.2, 3.4, 4.7, 2.8, 2.6, 4.3, 4.1)
B <- c(3.8, 1.9, 1.5, 3.9, 3.7, 3.8, 4.7, 2.9, 2.7, 4.5, 4.3, 2.8, 2.5, 3.5, 4.5, 3, 2.4)
X <- c(4.5, 5, 2.1, 4.9, 2.7, 2.4, 4.3, 4.9, 3.3, 4.9, 3, 2.8, 4.8,2.8, 4.8, 5.1, 3.1)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1")
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B \nCond 50-50", xlab = "Trial", ylab = "Causal rating score")
A <- Cond000$A
B <- Cond000$B
X <- Cond000$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1")
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```

### Cond 000 Thicker lines
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 50-50", xlab = "Trial", ylab = "Causal rating score")
A <- c(4.9, 5, 5.1, 3.2, 2.8, 2.4, 2.2, 4.5, 4, 3, 2.2, 3.4, 4.7, 2.8, 2.6, 4.3, 4.1)
B <- c(3.8, 1.9, 1.5, 3.9, 3.7, 3.8, 4.7, 2.9, 2.7, 4.5, 4.3, 2.8, 2.5, 3.5, 4.5, 3, 2.4)
X <- c(4.5, 5, 2.1, 4.9, 2.7, 2.4, 4.3, 4.9, 3.3, 4.9, 3, 2.8, 4.8,2.8, 4.8, 5.1, 3.1)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1", lwd = 2)
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd = 2)
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd =2)
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B \nCond 50-50", xlab = "Trial", ylab = "Causal rating score")
A <- Cond000$A
B <- Cond000$B
X <- Cond000$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1", lwd = 2)
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd =2 )
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd = 2)
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```

### Cond 000 SE
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 50-50", xlab = "Trial", ylab = "Causal rating score")
A <- c(4.9, 5, 5.1, 3.2, 2.8, 2.4, 2.2, 4.5, 4, 3, 2.2, 3.4, 4.7, 2.8, 2.6, 4.3, 4.1)
B <- c(3.8, 1.9, 1.5, 3.9, 3.7, 3.8, 4.7, 2.9, 2.7, 4.5, 4.3, 2.8, 2.5, 3.5, 4.5, 3, 2.4)
X <- c(4.5, 5, 2.1, 4.9, 2.7, 2.4, 4.3, 4.9, 3.3, 4.9, 3, 2.8, 4.8,2.8, 4.8, 5.1, 3.1)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1")
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B \nCond 50-50, with SE", xlab = "Trial", ylab = "Causal rating score")
A <- Cond000$A
B <- Cond000$B
X <- Cond000$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1")
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
errorbars(x= c(1:16), y = Cond000$A, top = SETrials000A, bottom = SETrials000A, add = TRUE, length = 0.05)
errorbars(x= c(1:16), y = Cond000$B, top = SETrials000B, bottom = SETrials000B, add = TRUE, length = 0.05)
errorbars(x= c(1:16), y = Cond000$X, top = SETrials000X, bottom = SETrials000X, add = TRUE, length = 0.05)
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```

### Cond 050 
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 75-25", xlab = "Trial", ylab = "Causal rating score")
A <- c(4.7,5,4.6,3.6,5,3.2,4.4,5.5,4.9,3.9,5.4,4.8,5.5,3.8,4.7,5.7,5.6)
B <- c(4.5,2,1.9,4.2,2.6,3.3,2,1.9,1.8,3.3,2.2,2,1.8,2.5,1.5,1.3,1)
X <- c(3.8,4.6,2.8,4.5,5,3.1,2.7,4.5,3,4.8,5.1,3.3,4.8,3.2,2.8,4.2,2.9)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1")
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B \nCond 75-25", xlab = "Trial", ylab = "Causal rating score")
A <- Cond050$A
B <- Cond050$B
X <- Cond050$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1")
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```

### Cond 050 Thicker lines 
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 75-25", xlab = "Trial", ylab = "Causal rating score")
A <- c(4.7,5,4.6,3.6,5,3.2,4.4,5.5,4.9,3.9,5.4,4.8,5.5,3.8,4.7,5.7,5.6)
B <- c(4.5,2,1.9,4.2,2.6,3.3,2,1.9,1.8,3.3,2.2,2,1.8,2.5,1.5,1.3,1)
X <- c(3.8,4.6,2.8,4.5,5,3.1,2.7,4.5,3,4.8,5.1,3.3,4.8,3.2,2.8,4.2,2.9)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1", lwd = 2)
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd =2)
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd = 2)
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B \nCond 75-25", xlab = "Trial", ylab = "Causal rating score")
A <- Cond050$A
B <- Cond050$B
X <- Cond050$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1", lwd = 2)
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd =2)
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd =2)
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```

### Cond 050 
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 75-25", xlab = "Trial", ylab = "Causal rating score")
A <- c(4.7,5,4.6,3.6,5,3.2,4.4,5.5,4.9,3.9,5.4,4.8,5.5,3.8,4.7,5.7,5.6)
B <- c(4.5,2,1.9,4.2,2.6,3.3,2,1.9,1.8,3.3,2.2,2,1.8,2.5,1.5,1.3,1)
X <- c(3.8,4.6,2.8,4.5,5,3.1,2.7,4.5,3,4.8,5.1,3.3,4.8,3.2,2.8,4.2,2.9)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1")
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B \nCond 75-25, with SE", xlab = "Trial", ylab = "Causal rating score")
A <- Cond050$A
B <- Cond050$B
X <- Cond050$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1")
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
errorbars(x= c(1:16), y = Cond050$A, top = SETrials050A, bottom = SETrials050A, add = TRUE, length = 0.05)
errorbars(x= c(1:16), y = Cond050$B, top = SETrials050B, bottom = SETrials050B, add = TRUE, length = 0.05)
errorbars(x= c(1:16), y = Cond050$X, top = SETrials050X, bottom = SETrials050X, add = TRUE, length = 0.05)
legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```

### Cond 100 
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 100-0", xlab = "Trial", ylab = "Causal rating score")
A <- c(5.1,5.2,4.9,5.1,6.2,6.3,6,6.6,6.5,6.5,7,6.6,7.1,7.2,7,7.2,7.2)
B <- c(4.5,2.1,1.5,1.3,1.2,1.1,1,1,0.9,0.7,0.8,0.7,0.8,0.7,0.6,0.7,0.5)
X <- c(3.6,4.5,2.2,1.8,3,3.3,2,3.1,1.7,1.5,2.5,1.4,2.3,2.5,1.4,2.3,1.4)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1")
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B\nCond 100-0", xlab = "Trial", ylab = "Causal rating score")
A <- Cond100$A
B <- Cond100$B
X <- Cond100$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1")
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen")

legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```

### Cond 100 Thicker lines
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 100-0", xlab = "Trial", ylab = "Causal rating score")
A <- c(5.1,5.2,4.9,5.1,6.2,6.3,6,6.6,6.5,6.5,7,6.6,7.1,7.2,7,7.2,7.2)
B <- c(4.5,2.1,1.5,1.3,1.2,1.1,1,1,0.9,0.7,0.8,0.7,0.8,0.7,0.6,0.7,0.5)
X <- c(3.6,4.5,2.2,1.8,3,3.3,2,3.1,1.7,1.5,2.5,1.4,2.3,2.5,1.4,2.3,1.4)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1", lwd = 2)
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd = 2)
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd = 2)
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B\nCond 100-0", xlab = "Trial", ylab = "Causal rating score")
A <- Cond100$A
B <- Cond100$B
X <- Cond100$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1", lwd = 2)
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1", lwd =2)
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen", lwd = 2)

legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```

### Cond 100 
```{r}
par(mfrow = c(1,2))
par(las=1)
#original plot
emptyPlot(c(0,16),c(0,8), xmark = c(1,4,8,12,16), ymark=c(0,1,2,3,4,5,6,7,8), bty='n', main = "Van Hamme & Wasserman 1994 \nCond 100-0", xlab = "Trial", ylab = "Causal rating score")
A <- c(5.1,5.2,4.9,5.1,6.2,6.3,6,6.6,6.5,6.5,7,6.6,7.1,7.2,7,7.2,7.2)
B <- c(4.5,2.1,1.5,1.3,1.2,1.1,1,1,0.9,0.7,0.8,0.7,0.8,0.7,0.6,0.7,0.5)
X <- c(3.6,4.5,2.2,1.8,3,3.3,2,3.1,1.7,1.5,2.5,1.4,2.3,2.5,1.4,2.3,1.4)
points(c(0:16),A, pch = 0, type = "b", col = "indianred1")
points(c(0:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(0:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
abline(v=0.5, col="grey", lty = 1)
legend(0.05,8,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

emptyPlot(c(0,16),c(1,9), xmark = c(1,4,8,12,16), ymark=c(1,2,3,4,5,6,7,8, 9), bty='n', main = "Our Experiment 1B\nCond 100-0, with SE", xlab = "Trial", ylab = "Causal rating score")
A <- Cond100$A
B <- Cond100$B
X <- Cond100$X
points(c(1:16),A, pch = 0, type = "b", col = "indianred1")
points(c(1:16),B, pch =16, type = "b", lty = 2, col = "steelblue1")
points(c(1:16),X, pch =15, type = "b", lty = 4, col = "limegreen")
errorbars(x= c(1:16), y = Cond100$A, top = SETrials100A, bottom = SETrials100A, add = TRUE, length = 0.05)
errorbars(x= c(1:16), y = Cond100$B, top = SETrials100B, bottom = SETrials100B, add = TRUE, length = 0.05)
errorbars(x= c(1:16), y = Cond100$X, top = SETrials100X, bottom = SETrials100X, add = TRUE, length = 0.05)

legend(0.05,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```




```{r}
#I'm sampling 3 here
#sample(unique(dat$prolific_id), 3, replace = TRUE)
#"5ffa1ea174ea4b3b304bef6a" "5bc79f652885710001a0e82a" "60021cc6d5be39201d34f6bf"
#so I'll plot those three people
P1 <- subset(train, train$prolific_id == "5ffa1ea174ea4b3b304bef6a")
P2 <- subset(train, train$prolific_id == "5bc79f652885710001a0e82a")
P3 <- subset(train, train$prolific_id == "5ec7ec8d0125920a254a6cfa")
```

```{r}
#p1 had Cond 50, 100, 0
par(mfrow = c(1,1))
par(las = 1)
emptyPlot(c(1,60), c(1,9), xmark = c(1,16,32,48), ymark= c(1,2,3,4,5,6,7,8,9), bty = 'n', main = "Participant 1 Training phase run\n Experiment 1B", xlab = "", ylab = "Causal rating score")
points(c(1:16), P1$responseR1[P1$blockNr == "Block1"], type = 'l', col = "red", lty = 1, lwd = 1)
points(c(1:16), P1$responseR2[P1$blockNr == "Block1"], type = 'l', col = "black", lty = 1, lwd = 1)
points(c(1:16), P1$responseR3[P1$blockNr == "Block1"], type = 'l', col = "green", lty = 1, lwd = 1)
points(c(17:32), P1$responseR1[P1$blockNr == "Block2"], type = 'l', col = "grey", lty = 1, lwd = 1)
points(c(17:32), P1$responseR2[P1$blockNr == "Block2"], type = 'l', col = "cyan", lty = 1, lwd = 1)
points(c(17:32), P1$responseR3[P1$blockNr == "Block2"], type = 'l', col = "pink", lty = 1, lwd = 1)
points(c(33:48), P1$responseR1[P1$blockNr == "Block3"], type = 'l', col = "brown", lty = 1, lwd = 1)
points(c(33:48), P1$responseR2[P1$blockNr == "Block3"], type = 'l', col = "yellow2", lty = 1, lwd = 1)
points(c(33:48), P1$responseR3[P1$blockNr == "Block3"], type = 'l', col = "orange", lty = 1, lwd = 1)
mtext("75-25", side = 1, at = 8, line = 2.5)
mtext("100-0", side = 1, at = 24, line = 2.5)
mtext("50-50", side = 1, at = 40, line = 2.5)


#still P1
par(mfrow = c(1,1))
par(las = 1)
emptyPlot(c(1,60), c(1,9), xmark = c(1,16,32,48), ymark= c(1,2,3,4,5,6,7,8,9), bty = 'n', main = "Participant 1 Training phase run\n Experiment 1B", xlab = "", ylab = "Causal rating score")
points(c(1:48), P1$responseR1, type = 'l', col = "indianred1", lty = 1, lwd = 1)
points(c(1:48), P1$responseR2, type = 'l', col = "steelblue1", lty = 1, lwd = 1)
points(c(1:48), P1$responseR3, type = 'l', col = "limegreen", lty = 1, lwd = 1)
mtext("75-25", side = 1, at = 8, line = 2.5)
mtext("100-0", side = 1, at = 24, line = 2.5)
mtext("50-50", side = 1, at = 40, line = 2.5)
legend(0.02,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))

```
```{r}
#p2 had Cond 50, 100, 0.
par(mfrow = c(1,1))
par(las = 1)
emptyPlot(c(1,60), c(1,9), xmark = c(1,16,32,48), ymark= c(1,2,3,4,5,6,7,8,9), bty = 'n', main = "Participant 2 Training phase run\n Experiment 1B", xlab = "", ylab = "Causal rating score")
points(c(1:16), P2$responseR1[P2$blockNr == "Block1"], type = 'l', col = "red", lty = 1, lwd = 1)
points(c(1:16), P2$responseR2[P2$blockNr == "Block1"], type = 'l', col = "black", lty = 1, lwd = 1)
points(c(1:16), P2$responseR3[P2$blockNr == "Block1"], type = 'l', col = "green", lty = 1, lwd = 1)
points(c(17:32), P2$responseR1[P2$blockNr == "Block2"], type = 'l', col = "grey", lty = 1, lwd = 1)
points(c(17:32), P2$responseR2[P2$blockNr == "Block2"], type = 'l', col = "cyan", lty = 1, lwd = 1)
points(c(17:32), P2$responseR3[P2$blockNr == "Block2"], type = 'l', col = "pink", lty = 1, lwd = 1)
points(c(33:48), P2$responseR1[P2$blockNr == "Block3"], type = 'l', col = "brown", lty = 1, lwd = 1)
points(c(33:48), P2$responseR2[P2$blockNr == "Block3"], type = 'l', col = "yellow2", lty = 1, lwd = 1)
points(c(33:48), P2$responseR3[P2$blockNr == "Block3"], type = 'l', col = "orange", lty = 1, lwd = 1)
mtext("75-25", side = 1, at = 8, line = 2.5)
mtext("100-0", side = 1, at = 24, line = 2.5)
mtext("50-50", side = 1, at = 40, line = 2.5)


#still P2
par(mfrow = c(1,1))
par(las = 1)
emptyPlot(c(1,60), c(1,9), xmark = c(1,16,32,48), ymark= c(1,2,3,4,5,6,7,8,9), bty = 'n', main = "Participant 2 Training phase run\n Experiment 1B", xlab = "", ylab = "Causal rating score")
points(c(1:48), P2$responseR1, type = 'l', col = "indianred1", lty = 1, lwd = 1)
points(c(1:48), P2$responseR2, type = 'l', col = "steelblue1", lty = 1, lwd = 1)
points(c(1:48), P2$responseR3, type = 'l', col = "limegreen", lty = 1, lwd = 1)
mtext("75-25", side = 1, at = 8, line = 2.5)
mtext("100-0", side = 1, at = 24, line = 2.5)
mtext("50-50", side = 1, at = 40, line = 2.5)
legend(0.02,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```
```{r}
#p3 had Cond 100, 0, 50.
par(mfrow = c(1,1))
par(las = 1)
emptyPlot(c(1,60), c(1,9), xmark = c(1,16,32,48), ymark= c(1,2,3,4,5,6,7,8,9), bty = 'n', main = "Participant 3 Training phase run\n Experiment 1B", xlab = "", ylab = "Causal rating score")
points(c(1:16), P3$responseR1[P3$blockNr == "Block1"], type = 'l', col = "red", lty = 1, lwd = 1)
points(c(1:16), P3$responseR2[P3$blockNr == "Block1"], type = 'l', col = "black", lty = 1, lwd = 1)
points(c(1:16), P3$responseR3[P3$blockNr == "Block1"], type = 'l', col = "green", lty = 1, lwd = 1)
points(c(17:32), P3$responseR1[P3$blockNr == "Block2"], type = 'l', col = "grey", lty = 1, lwd = 1)
points(c(17:32), P3$responseR2[P3$blockNr == "Block2"], type = 'l', col = "cyan", lty = 1, lwd = 1)
points(c(17:32), P3$responseR3[P3$blockNr == "Block2"], type = 'l', col = "pink", lty = 1, lwd = 1)
points(c(33:48), P3$responseR1[P3$blockNr == "Block3"], type = 'l', col = "brown", lty = 1, lwd = 1)
points(c(33:48), P3$responseR2[P3$blockNr == "Block3"], type = 'l', col = "yellow2", lty = 1, lwd = 1)
points(c(33:48), P3$responseR3[P3$blockNr == "Block3"], type = 'l', col = "orange", lty = 1, lwd = 1)
mtext("100-0", side = 1, at = 8, line = 2.5)
mtext("50-50", side = 1, at = 24, line = 2.5)
mtext("75-25", side = 1, at = 40, line = 2.5)


#still P3
par(mfrow = c(1,1))
par(las = 1)
emptyPlot(c(1,60), c(1,9), xmark = c(1,16,32,48), ymark= c(1,2,3,4,5,6,7,8,9), bty = 'n', main = "Participant 3 Training phase run\n Experiment 1B", xlab = "", ylab = "Causal rating score")
points(c(1:48), P3$responseR1, type = 'l', col = "indianred1", lty = 1, lwd = 1)
points(c(1:48), P3$responseR2, type = 'l', col = "steelblue1", lty = 1, lwd = 1)
points(c(1:48), P3$responseR3, type = 'l', col = "limegreen", lty = 1, lwd = 1)
mtext("100-0", side = 1, at = 8, line = 2.5)
mtext("50-50", side = 1, at = 24, line = 2.5)
mtext("75-25", side = 1, at = 40, line = 2.5)
legend(0.02,9,legend =c("A", "B", "X"), pch = c(0,16,15), col = c("indianred1", "steelblue1", "limegreen"))
```
```{r}
#Calculating the average scores on the trials where "Diamond" was the outcome, and on trials where "No Diamond" was the outcome
#We would expect that the scores to the No Diamond would be lower on average
Diamond <- subset(train, train$Outcome == "Diamond.png")
NoDiamond <- subset(train, train$Outcome == "NoDiamond.png")

DiamondAvg <- aggregate(list(Diamond$responseR1, Diamond$responseR2, Diamond$responseR3), list(Diamond$Cond), mean, na.rm = T)
NoDiamondAvg <- aggregate(list(NoDiamond$responseR1, NoDiamond$responseR2, NoDiamond$responseR3), list(NoDiamond$Cond), mean, na.rm = T)
SE <- c(std.error(Diamond$responseR1[Diamond$Cond == "0"]), std.error(NoDiamond$responseR1[NoDiamond$Cond == "0"]), std.error(Diamond$responseR2[Diamond$Cond == "0"]), std.error(NoDiamond$responseR2[NoDiamond$Cond == "0"]), std.error(Diamond$responseR3[Diamond$Cond == "0"]), std.error(NoDiamond$responseR3[NoDiamond$Cond == "0"]),  std.error(Diamond$responseR1[Diamond$Cond == "50"]), std.error(NoDiamond$responseR1[NoDiamond$Cond == "50"]), std.error(Diamond$responseR2[Diamond$Cond == "50"]), std.error(NoDiamond$responseR2[NoDiamond$Cond == "50"]), std.error(Diamond$responseR3[Diamond$Cond == "50"]), std.error(NoDiamond$responseR3[NoDiamond$Cond == "50"]),  std.error(Diamond$responseR1[Diamond$Cond == "100"]), std.error(NoDiamond$responseR1[NoDiamond$Cond == "100"]), std.error(Diamond$responseR2[Diamond$Cond == "100"]), std.error(NoDiamond$responseR2[NoDiamond$Cond == "100"]), std.error(Diamond$responseR3[Diamond$Cond == "100"]), std.error(NoDiamond$responseR3[NoDiamond$Cond == "100"]))
colnames(DiamondAvg) <- c("Cond", "A", "B", "X")
colnames(NoDiamondAvg) <- c("Cond", "A", "B", "X")

DiamondAvg
NoDiamondAvg

par(mfrow = c(1,1))
par(las = 1)
emptyPlot(c(1,130), c(1,9.5), xaxt = "none", ymark= c(1,2,3,4,5,6, 7, 8,9), bty = 'n', main = "Average scores to Diamond and No Diamond Trials", xlab = "", ylab = "Causal rating score")
add_bars(x=c(0,5,15,20,30,35, 45,50,60,65,75,80, 90,95,105,110,120,125), y=c(DiamondAvg$A[DiamondAvg$Cond == "0"], NoDiamondAvg$A[NoDiamondAvg$Cond == "0"], DiamondAvg$B[DiamondAvg$Cond == "0"], NoDiamondAvg$B[NoDiamondAvg$Cond == "0"],DiamondAvg$X[DiamondAvg$Cond == "0"], NoDiamondAvg$X[NoDiamondAvg$Cond == "0"], DiamondAvg$A[DiamondAvg$Cond == "50"], NoDiamondAvg$A[NoDiamondAvg$Cond == "50"], DiamondAvg$B[DiamondAvg$Cond == "50"], NoDiamondAvg$B[NoDiamondAvg$Cond == "50"],DiamondAvg$X[DiamondAvg$Cond == "50"], NoDiamondAvg$X[NoDiamondAvg$Cond == "50"], DiamondAvg$A[DiamondAvg$Cond == "100"], NoDiamondAvg$A[NoDiamondAvg$Cond == "100"], DiamondAvg$B[DiamondAvg$Cond == "100"], NoDiamondAvg$B[NoDiamondAvg$Cond == "100"],DiamondAvg$X[DiamondAvg$Cond == "100"], NoDiamondAvg$X[NoDiamondAvg$Cond == "100"]), width = 5, col = c("indianred1", "indianred1", "steelblue1", "steelblue1", "limegreen", "limegreen"), density = c(200,6))

errorbars(x=c(0,5,15,20,30,35, 45,50,60,65,75,80, 90,95,105,110,120,125), y=c(DiamondAvg$A[DiamondAvg$Cond == "0"], NoDiamondAvg$A[NoDiamondAvg$Cond == "0"], DiamondAvg$B[DiamondAvg$Cond == "0"], NoDiamondAvg$B[NoDiamondAvg$Cond == "0"],DiamondAvg$X[DiamondAvg$Cond == "0"], NoDiamondAvg$X[NoDiamondAvg$Cond == "0"], DiamondAvg$A[DiamondAvg$Cond == "50"], NoDiamondAvg$A[NoDiamondAvg$Cond == "50"], DiamondAvg$B[DiamondAvg$Cond == "50"], NoDiamondAvg$B[NoDiamondAvg$Cond == "50"],DiamondAvg$X[DiamondAvg$Cond == "50"], NoDiamondAvg$X[NoDiamondAvg$Cond == "50"], DiamondAvg$A[DiamondAvg$Cond == "100"], NoDiamondAvg$A[NoDiamondAvg$Cond == "100"], DiamondAvg$B[DiamondAvg$Cond == "100"], NoDiamondAvg$B[NoDiamondAvg$Cond == "100"],DiamondAvg$X[DiamondAvg$Cond == "100"], NoDiamondAvg$X[NoDiamondAvg$Cond == "100"]) , top = SE , bottom = SE, add = TRUE, length = .05)

abline(v=40, col="grey2", lty = 1)
abline(v=85, col="grey2", lty = 1)
#condition text
mtext("50-50", side = 1, at = 18, line = 1)
mtext("75-25", side = 1, at = 63, line = 1)
mtext("100-0", side = 1, at = 108, line = 1)
#letters
text(x=2.5, y = 7.3, labels = "A")
text(x=47.5, y = 7.3, labels = "A")
text(x=92.5, y = 7.3, labels = "A")
text(x=17.5, y = 7.3, labels = "B")
text(x=62.5, y = 7.3, labels = "B")
text(x=107.5, y = 7.3, labels = "B")
text(x=32.5, y = 7.3, labels = "X")
text(x=77.5, y = 7.3, labels = "X")
text(x=122.5, y = 7.3, labels = "X")
legend(x=0, y = 9.5, legend =c("Diamond", "No Diamond"), density = c(200,20), col= c("indianred1"))


#c("indianred1", "indianred3", "steelblue1", "steelblue3", "limegreen", "palegreen4"))

SE
range(SE)
```

```{r}
t.test(Diamond$responseR1[Diamond$Cond == "0"], NoDiamond$responseR1[NoDiamond$Cond == "0"], alternative = "two.sided", paired = FALSE) #sign, diamond higher than not diamond
t.test(Diamond$responseR2[Diamond$Cond == "0"], NoDiamond$responseR2[NoDiamond$Cond == "0"], alternative = "two.sided", paired = FALSE) #not sign
t.test(Diamond$responseR3[Diamond$Cond == "0"], NoDiamond$responseR3[NoDiamond$Cond == "0"], alternative = "two.sided", paired = FALSE) #sign, diamond higher than not diamond

t.test(Diamond$responseR1[Diamond$Cond == "50"], NoDiamond$responseR1[NoDiamond$Cond == "50"], alternative = "two.sided", paired = FALSE) #sign, diamond higher than not diamond
t.test(Diamond$responseR2[Diamond$Cond == "50"], NoDiamond$responseR2[NoDiamond$Cond == "50"], alternative = "two.sided", paired = FALSE) #not sign
t.test(Diamond$responseR3[Diamond$Cond == "50"], NoDiamond$responseR3[NoDiamond$Cond == "50"], alternative = "two.sided", paired = FALSE) #sign, diamond higher than not diamond

t.test(Diamond$responseR1[Diamond$Cond == "100"], NoDiamond$responseR1[NoDiamond$Cond == "100"], alternative = "two.sided", paired = FALSE) #sign, diamond higher than not diamond
t.test(Diamond$responseR2[Diamond$Cond == "100"], NoDiamond$responseR2[NoDiamond$Cond == "100"], alternative = "two.sided", paired = FALSE) #not sign
t.test(Diamond$responseR3[Diamond$Cond == "100"], NoDiamond$responseR3[NoDiamond$Cond == "100"], alternative = "two.sided", paired = FALSE) #sign, diamond higher than not diamond
```
<br/> 
<br/>
These t-test show exactly what we would expect. The diamond trials are always scored higher than the no diamond trials. That is except for B. This makes sense though, because, B predicts an allergic outcome a lot less than the others. So here we would expect that people will start to score B lower overall, even on the trials where it does predict an allergic reaction. In the original one B in condition 50-50 was signficiantly different, but here it is not. <br/>
```{r}
table(train$CondFirstBlock)
```
I thought this might be due to the fact that less people saw condition 50-50 as their first block and therefore would have a bias already, but this does not necessarily seem to be the case.<br/>

## TEST PHASE

```{r}
#First getting the test phase data 
test <- dat[which(dat$Train_Test == "Test"),] 
test$responseR1[test$responseR1 == 999] <- NA
test$responseR2[test$responseR2 == 999] <- NA
test$responseR3[test$responseR3 == 999] <- NA

#And also splitting them into the different phases
testP1 <- test[which(test$Cond == "Phase1"),]
testP2 <- test[which(test$Cond == "Phase2"),]
testP3 <- test[which(test$Cond == "Phase3"),]
```

### Phase 1
<br/> This phase was in the same order for each participant. At first the cues from the first block were seen, then a new cue (together with X of the first block) and then those of the third block were seen. This time participants were asked how likely they thought these items would lead to outcome Y, with Y being either a diamond (which they've seen before) or a fossil (a new outcome)
```{r}
#Phase 1

#I want to look at the outcome to fossil and that to diamond
testF <- testP1[which(testP1$Outcome == "Fossil.png"),]
testD <- testP1[which(testP1$Outcome == "Diamond.png"),]

#Now I want the average scores for A B and X for each of these outcomes, but also specifically A1, B1 etc. Therefore I will have to look at specific responses to trials. Therefore aggregate isn't very useful to use here.

#X
X1F <- testF[which(testF$Trial == 2 | testF$Trial == 4 | testF$Trial == 6),]
avgX1F <- mean(X1F$responseR2, na.rm = T)
X1D <- testD[which(testD$Trial == 1 | testD$Trial == 3 | testD$Trial == 5),]
avgX1D <- mean(X1D$responseR2, na.rm = T)
X3F <- testF[which(testF$Trial == 8 | testF$Trial == 10),]
avgX3F <- mean(X3F$responseR2, na.rm = T)
X3D <- testD[which(testD$Trial == 7 | testD$Trial == 9),]
avgX3D <- mean(X3D$responseR2, na.rm = T)

#A
A1F <- testF[which(testF$Trial == 2),]
avgA1F <- mean(A1F$responseR1, na.rm = T)
A1D <- testD[which(testD$Trial == 1),]
avgA1D <- mean(A1D$responseR1, na.rm = T)

A3F <- testF[which(testF$Trial == 8),]
avgA3F <- mean(A3F$responseR1, na.rm = T)
A3D <- testD[which(testD$Trial == 7),]
avgA3D <- mean(A3D$responseR1, na.rm = T)

#B
B1F <- testF[which(testF$Trial == 4),]
avgB1F <- mean(B1F$responseR1, na.rm = T)
B1D <- testD[which(testD$Trial == 3),]
avgB1D <- mean(B1D$responseR1, na.rm = T)

B3F <- testF[which(testF$Trial == 10),]
avgB3F <- mean(B3F$responseR1, na.rm = T)
B3D <- testD[which(testD$Trial == 9),]
avgB3D <- mean(B3D$responseR1, na.rm = T)

#C
CF <- testF[which(testF$Trial == 6),]
avgCF <- mean(CF$responseR1, na.rm = T)
CD <- testD[which(testD$Trial == 5),]
avgCD <- mean(CD$responseR1, na.rm = T)


Cue <- c("A1", "B1", "X1", "C", "A3", "B3", "X3")
Diamond <- c(avgA1D, avgB1D, avgX1D, avgCD, avgA3D, avgB3D, avgX3D)
Fossil <- c(avgA1F, avgB1F, avgX1F, avgCF, avgA3F, avgB3F, avgX3F)
Phase1 <- data.frame(Cue, Diamond, Fossil)
Phase1

``` 
<br/>
So there are some differences between scoring to diamond (seems a lot higher, expect for C and B3) and Fossil. The thing here is though that these are all categories collapsed. Later we will split those categories and see what happens then. <br />
Now I'll get the scores over the entire block.

```{r}
#now that we know what was asked when in the training phase 

ABl1 <- mean(train$responseR1[train$blockNr == "Block1" & train$Trial == 15], na.rm = T)
BBl1 <- mean(train$responseR2[train$blockNr == "Block1" & train$Trial == 16], na.rm = T)
XBl1 <- mean(train$responseR3[train$blockNr == "Block1" & train$Trial == 16], na.rm = T)

ABl3 <- mean(train$responseR1[train$blockNr == "Block3" & train$Trial == 15], na.rm = T)
BBl3 <- mean(train$responseR2[train$blockNr == "Block3" & train$Trial == 16], na.rm = T)
XBl3 <- mean(train$responseR3[train$blockNr == "Block3" & train$Trial == 16], na.rm = T)

Cues <- c("A1", "B1", "X1", "A3", "B3", "X3")
Mean <- c(ABl1, BBl1, XBl1, ABl3, BBl3, XBl3)
TrainAvgBl1_3 <- data.frame(Cues, Mean) 
TrainAvgBl1_3

Original <- c(ABl1, BBl1, XBl1, "NA", ABl3, BBl3, XBl3)
Phase1$Original <- as.numeric(Original)
Phase1

```
<br/> Here we can see the differences in scores to diamond in the test phase (1), fossil (test phase 1) and the original scores to A, B and X in block 1 and 3. This is averaged over all conditions. We will now perform t-tests to see if there is a difference between these values.


```{r}
#1) Are there significant differences between A, B and X when asked in their original block 1 and in the test phase
t.test(A1D$responseR1, train$responseR1[train$blockNr == "Block1" & train$Trial == 15], alternative = "two.sided", paired = FALSE) #sign, decrease
t.test(B1D$responseR1, train$responseR2[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = FALSE) #no sign             (DIFF FROM 1)
t.test(X1D$responseR2, train$responseR3[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = FALSE) #sign diff, increase


#2) Are there sign differences between A, B and X when asked in block 3 and in the test phase
t.test(A3D$responseR1, train$responseR1[train$blockNr == "Block3" & train$Trial == 15], alternative = "two.sided", paired = FALSE) #no diff 
t.test(B3D$responseR1, train$responseR2[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = FALSE) #no diff
t.test(X3D$responseR2, train$responseR3[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = FALSE) #no diff



#3) Is there a sign difference between the C value and that of A B and X in the test phase 
t.test(CD$responseR1, A3D$responseR1, alternative = "two.sided", paired = FALSE) #sign diff C is lower
t.test(CD$responseR1, B3D$responseR1, alternative = "two.sided", paired = FALSE) #no sign diff
t.test(CD$responseR1, X3D$responseR2, alternative = "two.sided", paired = FALSE) #sign diff, score to C is lower 


t.test(CD$responseR1, A1D$responseR1, alternative = "two.sided", paired = FALSE) #sign diff, C is lower               (DIFF FROM 1)
t.test(CD$responseR1, B1D$responseR1, alternative = "two.sided", paired = FALSE) #sign diff, C lower 
t.test(CD$responseR1, X1D$responseR2, alternative = "two.sided", paired = FALSE) #sign diff, score to C is lower

#4) Is there a difference between the ratings to fossil and those to diamond?
t.test(A1D$responseR1, A1F$responseR1, alternative = "two.sided", paired = FALSE) #not sign (marginally, then fossil lower than diamond)
t.test(B1D$responseR1, B1F$responseR1, alternative = "two.sided", paired = FALSE) #sign, lower score on the fossil than on the diamond
t.test(X1D$responseR2, X1F$responseR2, alternative = "two.sided", paired = FALSE) #sign, lower score on the fossil than on the diamond
t.test(CD$responseR1, CF$responseR1, alternative = "two.sided", paired = FALSE)   #no sign (makes sense! The cue is new)
t.test(A3D$responseR1, A3F$responseR1, alternative = "two.sided", paired = FALSE) #sign, lower score on the fossil than on the diamond
t.test(B3D$responseR1, B3F$responseR1, alternative = "two.sided", paired = FALSE) #not sign                                                     (DIFF FROM 1)
t.test(X3D$responseR2, X3F$responseR2, alternative = "two.sided", paired = FALSE) #sign, lower score fossil than on diamond                     (DIFF FROM 1)





#OLD###################################################################################################################################
#1) Are there significant differences between A, B and X when asked in their original block 1 and in the test phase
#t.test(A1D$responseR1, train$responseR1[train$blockNr == "Block1"], alternative = "two.sided", paired = FALSE) #no sign
#t.test(B1D$responseR1, train$responseR2[train$blockNr == "Block1"], alternative = "two.sided", paired = FALSE) #no sign             (DIFF FROM 1)
#t.test(X1D$responseR2, train$responseR3[train$blockNr == "Block1"], alternative = "two.sided", paired = FALSE) #sign diff, increase


#2) Are there sign differences between A, B and X when asked in block 3 and in the test phase
#t.test(A3D$responseR1, train$responseR1[train$blockNr == "Block3"], alternative = "two.sided", paired = FALSE) #sign diff, increase
#t.test(B3D$responseR1, train$responseR2[train$blockNr == "Block3"], alternative = "two.sided", paired = FALSE) #no diff
#t.test(X3D$responseR2, train$responseR3[train$blockNr == "Block3"], alternative = "two.sided", paired = FALSE) #no diff

#The only difference in significance is that of B1 in this experiment versus in the older one. In both block 1 and block 2 there is only one response significantly different when looking at the diamond trails vs the original scores. This does not really indicate one model or the other


#3) Is there a sign difference between the C value and that of A B and X in the test phase 
#t.test(CD$responseR1, train$responseR1[train$blockNr == "Block3"], alternative = "two.sided", paired = FALSE) #sign diff, score to C is lower
#t.test(CD$responseR1, train$responseR2[train$blockNr == "Block3"], alternative = "two.sided", paired = FALSE) #no sign diff
#t.test(CD$responseR1, train$responseR3[train$blockNr == "Block3"], alternative = "two.sided", paired = FALSE) #sign diff, score to C is lower


#t.test(CD$responseR1, train$responseR1[train$blockNr == "Block1"], alternative = "two.sided", paired = FALSE) #sign diff, score to C is lower
#t.test(CD$responseR1, train$responseR2[train$blockNr == "Block1"], alternative = "two.sided", paired = FALSE) #sign diff, score to C is lower     (DIFF FROM 1)
#t.test(CD$responseR1, train$responseR3[train$blockNr == "Block1"], alternative = "two.sided", paired = FALSE) #sign diff, score to C is lower

#this seems to indicate that the rescorla-wagner model is going on, as most score higher than the neutral cue, while the others are not different.


#4) Is there a difference between the ratings to fossil and those to diamond?
#t.test(A1D$responseR1, A1F$responseR1, alternative = "two.sided", paired = FALSE) #not sign (marginally, then fossil lower than diamond)
#t.test(B1D$responseR1, B1F$responseR1, alternative = "two.sided", paired = FALSE) #sign, lower score on the fossil than on the diamond
#t.test(X1D$responseR2, X1F$responseR2, alternative = "two.sided", paired = FALSE) #sign, lower score on the fossil than on the diamond
#t.test(CD$responseR1, CF$responseR1, alternative = "two.sided", paired = FALSE)   #no sign (makes sense! The cue is new)
#t.test(A3D$responseR1, A3F$responseR1, alternative = "two.sided", paired = FALSE) #sign, lower score on the fossil than on the diamond
#t.test(B3D$responseR1, B3F$responseR1, alternative = "two.sided", paired = FALSE) #not sign                                                     (DIFF FROM 1)
#t.test(X3D$responseR2, X3F$responseR2, alternative = "two.sided", paired = FALSE) #sign, lower score fossil than on diamond                     (DIFF FROM 1)

#okay so for this it seems that especially in the block that was the furthest away, a new outcome is scored much lower than the already seen one. As for a completely new cue there is no difference between a new or an old outcome.
#for cues that were seen more recently it seems that a new outcome has less of an influence in scoring




```
<br/>
<br/>
What I now want to do is split this into the seperate conditions

```{r, splitting the test phases into conditions}
testFSplit <- aggregate(list(testF$responseR1, testF$responseR2), list(testF$CondFirstBlock, testF$CondThirdBlock, testF$Trial), mean, na.rm = T)
colnames(testFSplit) <- c("Cond1", "Cond3", "Trial", "Response1", "Response2")
testDSplit <- aggregate(list(testD$responseR1, testD$responseR2), list(testD$CondFirstBlock, testD$CondThirdBlock, testD$Trial), mean, na.rm = T)
colnames(testDSplit) <- c("Cond1", "Cond3", "Trial", "Response1", "Response2")

#for each item we want the trials that belong to the first or third cue, and then take those purely from one condition

#X000
X1F000 <- testFSplit[which( (testFSplit$Trial == 2 | testFSplit$Trial == 4 | testFSplit$Trial == 6) & testFSplit$Cond1 == "0") ,]
avgX1F000 <- mean(X1F000$Response2, na.rm = T)
X1D000 <- testDSplit[which( (testDSplit$Trial == 1 | testDSplit$Trial == 3 | testDSplit$Trial == 5) & testDSplit$Cond1 == "0") ,]
avgX1D000 <- mean(X1D000$Response2, na.rm = T)

X3F000 <- testFSplit[which( (testFSplit$Trial == 8 | testFSplit$Trial == 10) & testFSplit$Cond3 == "0"),]
avgX3F000 <- mean(X3F000$Response2, na.rm = T)
X3D000 <- testDSplit[which( (testDSplit$Trial == 7 | testDSplit$Trial == 9) & testDSplit$Cond3 == "0"),]
avgX3D000 <- mean(X3D000$Response2, na.rm = T)

#X050
X1F050 <- testFSplit[which( (testFSplit$Trial == 2 | testFSplit$Trial == 4 | testFSplit$Trial == 6) & testFSplit$Cond1 == "50") ,]
avgX1F050 <- mean(X1F050$Response2, na.rm = T)
X1D050 <- testDSplit[which( (testDSplit$Trial == 1 | testDSplit$Trial == 3 | testDSplit$Trial == 5) & testDSplit$Cond1 == "50") ,]
avgX1D050 <- mean(X1D050$Response2, na.rm = T)

X3F050 <- testFSplit[which( (testFSplit$Trial == 8 | testFSplit$Trial == 10) & testFSplit$Cond3 == "50"),]
avgX3F050 <- mean(X3F050$Response2, na.rm = T)
X3D050 <- testDSplit[which( (testDSplit$Trial == 7 | testDSplit$Trial == 9) & testDSplit$Cond3 == "50"),]
avgX3D050 <- mean(X3D050$Response2, na.rm = T)

#X100
X1F100 <- testFSplit[which( (testFSplit$Trial == 2 | testFSplit$Trial == 4 | testFSplit$Trial == 6) & testFSplit$Cond1 == "100") ,]
avgX1F100 <- mean(X1F100$Response2, na.rm = T)
X1D100 <- testDSplit[which( (testDSplit$Trial == 1 | testDSplit$Trial == 3 | testDSplit$Trial == 5) & testDSplit$Cond1 == "100") ,]
avgX1D100 <- mean(X1D100$Response2, na.rm = T)

X3F100 <- testFSplit[which( (testFSplit$Trial == 8 | testFSplit$Trial == 10) & testFSplit$Cond3 == "100"),]
avgX3F100 <- mean(X3F100$Response2, na.rm = T)
X3D100 <- testDSplit[which( (testDSplit$Trial == 7 | testDSplit$Trial == 9) & testDSplit$Cond3 == "100"),]
avgX3D100 <- mean(X3D100$Response2, na.rm = T)

#######################################
#A000
A1F000 <- testFSplit[which( (testFSplit$Trial == 2 ) & testFSplit$Cond1 == "0") ,]
avgA1F000 <- mean(A1F000$Response1, na.rm = T)
A1D000 <- testDSplit[which( (testDSplit$Trial == 1) & testDSplit$Cond1 == "0") ,]
avgA1D000 <- mean(A1D000$Response1, na.rm = T)

A3F000 <- testFSplit[which( (testFSplit$Trial == 8) & testFSplit$Cond3 == "0"),]
avgA3F000 <- mean(A3F000$Response1, na.rm = T)
A3D000 <- testDSplit[which( (testDSplit$Trial == 7) & testDSplit$Cond3 == "0"),]
avgA3D000 <- mean(A3D000$Response1, na.rm = T)

#A050
A1F050 <- testFSplit[which( (testFSplit$Trial == 2) & testFSplit$Cond1 == "50") ,]
avgA1F050 <- mean(A1F050$Response1, na.rm = T)
A1D050 <- testDSplit[which( (testDSplit$Trial == 1) & testDSplit$Cond1 == "50") ,]
avgA1D050 <- mean(A1D050$Response1, na.rm = T)

A3F050 <- testFSplit[which( (testFSplit$Trial == 8) & testFSplit$Cond3 == "50"),]
avgA3F050 <- mean(A3F050$Response1, na.rm = T)
A3D050 <- testDSplit[which( (testDSplit$Trial == 7) & testDSplit$Cond3 == "50"),]
avgA3D050 <- mean(A3D050$Response1, na.rm = T)

#A100
A1F100 <- testFSplit[which( (testFSplit$Trial == 2) & testFSplit$Cond1 == "100") ,]
avgA1F100 <- mean(A1F100$Response1, na.rm = T)
A1D100 <- testDSplit[which( (testDSplit$Trial == 1) & testDSplit$Cond1 == "100") ,]
avgA1D100 <- mean(A1D100$Response1, na.rm = T)

A3F100 <- testFSplit[which( (testFSplit$Trial == 8) & testFSplit$Cond3 == "100"),]
avgA3F100 <- mean(A3F100$Response1, na.rm = T)
A3D100 <- testDSplit[which( (testDSplit$Trial == 7) & testDSplit$Cond3 == "100"),]
avgA3D100 <- mean(A3D100$Response1, na.rm = T)

#######################################

#B000
B1F000 <- testFSplit[which( (testFSplit$Trial == 4) & testFSplit$Cond1 == "0") ,]
avgB1F000 <- mean(B1F000$Response1, na.rm = T)
B1D000 <- testDSplit[which( (testDSplit$Trial == 3) & testDSplit$Cond1 == "0") ,]
avgB1D000 <- mean(B1D000$Response1, na.rm = T)

B3F000 <- testFSplit[which( (testFSplit$Trial == 10) & testFSplit$Cond3 == "0"),]
avgB3F000 <- mean(B3F000$Response1, na.rm = T)
B3D000 <- testDSplit[which( (testDSplit$Trial == 9) & testDSplit$Cond3 == "0"),]
avgB3D000 <- mean(B3D000$Response1, na.rm = T)

#B050
B1F050 <- testFSplit[which( (testFSplit$Trial == 4) & testFSplit$Cond1 == "50") ,]
avgB1F050 <- mean(B1F050$Response1, na.rm = T)
B1D050 <- testDSplit[which( (testDSplit$Trial == 3) & testDSplit$Cond1 == "50") ,]
avgB1D050 <- mean(B1D050$Response1, na.rm = T)

B3F050 <- testFSplit[which( (testFSplit$Trial == 10) & testFSplit$Cond3 == "50"),]
avgB3F050 <- mean(B3F050$Response1, na.rm = T)
B3D050 <- testDSplit[which( (testDSplit$Trial == 9) & testDSplit$Cond3 == "50"),]
avgB3D050 <- mean(B3D050$Response1, na.rm = T)

#B100
B1F100 <- testFSplit[which( (testFSplit$Trial == 4) & testFSplit$Cond1 == "100") ,]
avgB1F100 <- mean(B1F100$Response1, na.rm = T)
B1D100 <- testDSplit[which( (testDSplit$Trial == 3) & testDSplit$Cond1 == "100") ,]
avgB1D100 <- mean(B1D100$Response1, na.rm = T)

B3F100 <- testFSplit[which( (testFSplit$Trial == 10) & testFSplit$Cond3 == "100"),]
avgB3F100 <- mean(B3F100$Response1, na.rm = T)
B3D100 <- testDSplit[which( (testDSplit$Trial == 9) & testDSplit$Cond3 == "100"),]
avgB3D100 <- mean(B3D100$Response1, na.rm = T)


#as C was never asked before we cannot really compare it over conditions
#C
CF <- testF[which(testF$Trial == 6),]
avgCF <- mean(CF$responseR1, na.rm = T)
CD <- testD[which(testD$Trial == 5),]
avgCD <- mean(CD$responseR1, na.rm = T)


Cue <- c("A1","A1","A1", "B1", "B1", "B1", "X1", "X1", "X1", "C", "A3", "A3", "A3", "B3", "B3", "B3", "X3", "X3", "X3")
Cond <- c("0", "50", "100", "0", "50", "100", "0", "50", "100", "NA", "0", "50", "100", "0", "50", "100", "0", "50", "100")
Diamond1 <- c(avgA1D000, avgA1D050, avgA1D100, avgB1D000, avgB1D050, avgB1D100, avgX1D000, avgX1D050, avgX1D100, avgCD, avgA3D000, avgA3D050, avgA3D100, avgB3D000, avgB3D050, avgB3D100, avgX3D000, avgX3D050, avgX3D100)
Fossil1 <- c(avgA1F000, avgA1F050, avgA1F100, avgB1F000, avgB1F050, avgB1F100, avgX1F000, avgX1F050, avgX1F100, avgCF, avgA3F000, avgA3F050, avgA3F100, avgB3F000, avgB3F050, avgB3F100, avgX3F000, avgX3F050, avgX3F100)
Phase1Split <- data.frame(Cue, Cond, Diamond1, Fossil1)
Phase1Split
```

```{r}
#and now to add on to that, the original ones

#now that we know what was asked when in the training phase 
ABl1000 <- mean(train$responseR1[train$blockNr == "Block1" & train$Cond == "0" & train$Trial == 16], na.rm = T)
ABl1050 <- mean(train$responseR1[train$blockNr == "Block1" & train$Cond == "50"& train$Trial == 16], na.rm = T)
ABl1100 <- mean(train$responseR1[train$blockNr == "Block1" & train$Cond == "100"& train$Trial == 16], na.rm = T)

BBl1000 <- mean(train$responseR2[train$blockNr == "Block1" & train$Cond == "0"& train$Trial == 16], na.rm = T)
BBl1050 <- mean(train$responseR2[train$blockNr == "Block1" & train$Cond == "50"& train$Trial == 16], na.rm = T)
BBl1100 <- mean(train$responseR2[train$blockNr == "Block1" & train$Cond == "100"& train$Trial == 16], na.rm = T)

XBl1000 <- mean(train$responseR3[train$blockNr == "Block1" & train$Cond == "0"& train$Trial == 16], na.rm = T)
XBl1050 <- mean(train$responseR3[train$blockNr == "Block1" & train$Cond == "50"& train$Trial == 16], na.rm = T)
XBl1100 <- mean(train$responseR3[train$blockNr == "Block1" & train$Cond == "100"& train$Trial == 16], na.rm = T)

ABl3000 <- mean(train$responseR1[train$blockNr == "Block3" & train$Cond == "0"& train$Trial == 16], na.rm = T)
ABl3050 <- mean(train$responseR1[train$blockNr == "Block3" & train$Cond == "50"& train$Trial == 16], na.rm = T)
ABl3100 <- mean(train$responseR1[train$blockNr == "Block3" & train$Cond == "100"& train$Trial == 16], na.rm = T)

BBl3000 <- mean(train$responseR2[train$blockNr == "Block3" & train$Cond == "0"& train$Trial == 16], na.rm = T)
BBl3050 <- mean(train$responseR2[train$blockNr == "Block3" & train$Cond == "50"& train$Trial == 16], na.rm = T)
BBl3100 <- mean(train$responseR2[train$blockNr == "Block3" & train$Cond == "100"& train$Trial == 16], na.rm = T)

XBl3000 <- mean(train$responseR3[train$blockNr == "Block3" & train$Cond == "0"& train$Trial == 16], na.rm = T)
XBl3050 <- mean(train$responseR3[train$blockNr == "Block3" & train$Cond == "50"& train$Trial == 16], na.rm = T)
XBl3100 <- mean(train$responseR3[train$blockNr == "Block3" & train$Cond == "100"& train$Trial == 16], na.rm = T)


Original <- c(ABl1000, ABl1050, ABl1100, BBl1000, BBl1050, BBl1100, XBl1000, XBl1050, XBl1100, "NA", ABl3000, ABl3050, ABl3100, BBl3000, BBl3050, BBl3100, XBl3000, XBl3050, XBl3100)
Phase1Split$Original <- as.numeric(Original)
Phase1Split
```
<br/> In this table we now see each cue, which condition they were originally asked in, their scores to diamond in the test phase, their scores to fossil in the test phase, and their score in their original block.

<br/>
First of all is there even a significan difference between the scores given to the different conditions for diamond?

```{r}
t.test(A1D000$Response1, A1D050$Response1, alternative = "two.sided", paired = FALSE) #no diff (marginally? Then 00 higher than 50)
#t.test(A1D050$Response1, A1D100$Response1, alternative = "two.sided", paired = FALSE) #NOT ENOUGH OBSERVATIONS
#t.test(A1D100$Response1, A1D000$Response1, alternative = "two.sided", paired = FALSE) #NOT ENOUGH OBSERVATIONS

t.test(B1D000$Response1, B1D050$Response1, alternative = "two.sided", paired = FALSE) #no diff 
#t.test(B1D050$Response1, B1D100$Response1, alternative = "two.sided", paired = FALSE) #NOT ENOUGH OBSERVATIONS
#t.test(B1D100$Response1, B1D000$Response1, alternative = "two.sided", paired = FALSE) #NOT ENOUGH OBSERVATIONS

t.test(X1D000$Response2, X1D050$Response2, alternative = "two.sided", paired = FALSE) #no diff 
t.test(X1D050$Response2, X1D100$Response2, alternative = "two.sided", paired = FALSE) #no diff
t.test(X1D100$Response2, X1D000$Response2, alternative = "two.sided", paired = FALSE) #no diff
```
<br/>
So for block one there are no significant differences in the scores between the different conditions. So it seems that for the first block, condition does not have an effect on the test phase. For condition 75-25 and 100-0 there were not enoug observations (1 for 100-0 and 2 for 75-25) to perform a t-test on, this makes sense as there are only 10 participants.
```{r}
#block 3
#t.test(A3D000$Response1, A3D050$Response1, alternative = "two.sided", paired = FALSE) #NOT ENOUGH OBSERVATIONS
t.test(A3D050$Response1, A3D100$Response1, alternative = "two.sided", paired = FALSE) #no diff
#t.test(A3D100$Response1, A3D000$Response1, alternative = "two.sided", paired = FALSE) #NOT ENOUGH OBSERVATIONS

#t.test(B3D000$Response1, B3D050$Response1, alternative = "two.sided", paired = FALSE) #NOT ENOUGH OBSERVATIONS
t.test(B3D050$Response1, B3D100$Response1, alternative = "two.sided", paired = FALSE) #no diff
#t.test(B3D100$Response1, B3D000$Response1, alternative = "two.sided", paired = FALSE) #NOT ENOUGH OBSERVATIONS

t.test(X3D000$Response2, X3D050$Response2, alternative = "two.sided", paired = FALSE) #no diff 
t.test(X3D050$Response2, X3D100$Response2, alternative = "two.sided", paired = FALSE) #no diff
t.test(X3D100$Response2, X3D000$Response2, alternative = "two.sided", paired = FALSE) #no diff
```
<br/> There are no signficant differences in the last block either, but here too there is an issue of there not being enough observations for A and B.
<br/>


```{r}
SE_FD <- c(std.error(A1D$responseR1), std.error(A1F$responseR1),std.error(B1D$responseR1), std.error(B1F$responseR1), std.error(X1D$responseR2), std.error(X1F$responseR2), std.error(CD$responseR1), std.error(CF$responseR1), std.error(A3D$responseR1), std.error(A3F$responseR1),std.error(B3D$responseR1), std.error(B3F$responseR1), std.error(X3D$responseR2), std.error(X3F$responseR2))

par(mfrow = c(1,1))
par(las = 1)
emptyPlot(c(1,100), c(1,9), xaxt = "none", ymark= c(1,2,3,4,5,6,7,8,9), bty = 'n', main = "Average scores to Diamond and Fossil trials\n in test phase 1", xlab = "", ylab = "Causal rating score")
add_bars(x=c(0,5,15,20,30,35,45,50,60,65,75,80,90,95), y=c(avgA1D, avgA1F, avgA1D, avgB1F, avgX1D, avgX1F, avgCD, avgCF, avgA3D, avgA3F, avgB3D, avgB3F, avgX3D, avgX3F), width = 5, col = c("indianred1", "indianred1", "steelblue1", "steelblue1", "limegreen", "limegreen","gold", "gold", "indianred1", "indianred1", "steelblue1", "steelblue1", "limegreen", "limegreen"), density = c(200,6))

errorbars(x=c(0,5,15,20,30,35,45,50,60,65,75,80,90,95), y=c(avgA1D, avgA1F, avgA1D, avgB1F, avgX1D, avgX1F, avgCD, avgCF, avgA3D, avgA3F, avgB3D, avgB3F, avgX3D, avgX3F) , top = SE_FD , bottom = SE_FD, add = TRUE, length = .05)

abline(v=40, col="grey2", lty = 1)
abline(v=55, col="grey2", lty = 1)
#condition text
mtext("Cues from block 1", side = 1, at = 17, line = 1)
mtext("New cue", side = 1, at = 47, line = 1)
mtext("Cues from block 3", side = 1, at = 77, line = 1)
#letters
text(x=2.5, y = 8, labels = "A")
text(x=17.5, y = 8, labels = "B")
text(x=32.5, y = 8, labels = "X")
text(x=47.5, y = 8, labels = "C")
text(x=62.5, y = 8, labels = "A")
text(x=77.5, y = 8, labels = "B")
text(x=92.5, y = 8, labels = "X")
legend(x=0, y = 7, legend =c("Diamond", "Fossil"), density = c(200,20))

```

### Phase 2
<br/>
In this phase participants saw the same stimuli as in Phase 1, but now in random order. We want to caclulate the average values of A, B and X to allergic and fever and see if they differ from those of Phase 1 (ideally they shouldnt).
```{r}
#Phase 2

#while the trials are in a different order this time around, Trial was a variable given to the _row_ in the table. So in order you will also see that it was "trials 9 then 4 then 8 for example.

#So we basically do the same as before but now I have to rename some things, because I still need stuff like X1F to compare with in a t.test.

testF2 <- testP2[which(testP2$Outcome == "Fossil.png"),]
testD2 <- testP2[which(testP2$Outcome == "Diamond.png"),]

#Now I want the average scores for A B and X for each of these outcomes, but also specifically A1, B1 etc. Therefore I will have to look at specific responses to trials. Therefore aggregate isn't very useful to use here.

#X
X1F2 <- testF2[which(testF2$Trial == 2 | testF2$Trial == 4 | testF2$Trial == 6),]
avgX1F2 <- mean(X1F2$responseR2, na.rm = T)
X1D2 <- testD2[which(testD2$Trial == 1 | testD2$Trial == 3 | testD2$Trial == 5),]
avgX1D2 <- mean(X1D2$responseR2, na.rm = T)
X3F2 <- testF2[which(testF2$Trial == 8 | testF2$Trial == 10),]
avgX3F2 <- mean(X3F2$responseR2, na.rm = T)
X3D2 <- testD2[which(testD2$Trial == 7 | testD2$Trial == 9),]
avgX3D2 <- mean(X3D2$responseR2, na.rm = T)

#A
A1F2 <- testF2[which(testF2$Trial == 2),]
avgA1F2 <- mean(A1F2$responseR1, na.rm = T)
A1D2 <- testD2[which(testD2$Trial == 1),]
avgA1D2 <- mean(A1D2$responseR1, na.rm = T)

A3F2 <- testF2[which(testF2$Trial == 8),]
avgA3F2 <- mean(A3F2$responseR1, na.rm = T)
A3D2 <- testD2[which(testD2$Trial == 7),]
avgA3D2 <- mean(A3D2$responseR1, na.rm = T)

#B
B1F2 <- testF2[which(testF2$Trial == 4),]
avgB1F2 <- mean(B1F2$responseR1, na.rm = T)
B1D2 <- testD2[which(testD2$Trial == 3),]
avgB1D2 <- mean(B1D2$responseR1, na.rm = T)

B3F2 <- testF2[which(testF2$Trial == 10),]
avgB3F2 <- mean(B3F2$responseR1, na.rm = T)
B3D2 <- testD2[which(testD2$Trial == 9),]
avgB3D2 <- mean(B3D2$responseR1, na.rm = T)

#C
CF2 <- testF2[which(testF2$Trial == 6),]
avgCF2 <- mean(CF2$responseR1, na.rm = T)
CD2 <- testD2[which(testD2$Trial == 5),]
avgCD2 <- mean(CD2$responseR1, na.rm = T)


Cue <- c("A1", "B1", "X1", "C", "A3", "B3", "X3")
Diamond2 <- c(avgA1D2, avgB1D2, avgX1D2, avgCD2, avgA3D2, avgB3D2, avgX3D2)
Fossil2 <- c(avgA1F2, avgB1F2, avgX1F2, avgCF2, avgA3F2, avgB3F2, avgX3F2)
Phase2 <- data.frame(Cue, Diamond2, Fossil2)
Phase2
Phase1_2 <- data.frame(Cue, Diamond, Fossil, Diamond2, Fossil2)
Phase1_2

```
<br/> From first glace there do seem to be some differences, especially betwen the fossil socres, but also between some diamond scores. Let's find out if they are significantly different:
```{r}
#All no diff, so there is no difference between the scores in Phase 2 and Phase 1 to Diamond
t.test(A1D$responseR1, A1D2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(B1D$responseR1, B1D2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(X1D$responseR2, X1D2$responseR2, alternative = "two.sided", paired = FALSE) # this scores is even exactly the same!!
t.test(CD$responseR1, CD2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(A3D$responseR1, A3D2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(B3D$responseR1, B3D2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(X3D$responseR2, X3D2$responseR2, alternative = "two.sided", paired = FALSE)

#all no diff too! So Phase 1 and 2 also don't differ in their scores to Fossil.
t.test(A1F$responseR1, A1F2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(B1F$responseR1, B1F2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(X1F$responseR2, X1F2$responseR2, alternative = "two.sided", paired = FALSE)
t.test(CF$responseR1, CF2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(A3F$responseR1, A3F2$responseR1, alternative = "two.sided", paired = FALSE) # this one also scores a p-value of 1, meaning exactly the same
t.test(B3F$responseR1, B3F2$responseR1, alternative = "two.sided", paired = FALSE)
t.test(X3F$responseR2, X3F2$responseR2, alternative = "two.sided", paired = FALSE)


```

### Phase 3
<br/> This phase introduced alternative versions of the stimuli (e.g instead of a mouse now a hamster), and reintroduced the "no diamond" outcome again.
<br/>

We want to know several things. The first being: what the average scores of the alternatives are and compare those to average of the original blocks?

```{r}
#Phase 3
testF3 <- testP3[which(testP3$Outcome == "Fossil.png"),]
testD3 <- testP3[which(testP3$Outcome == "Diamond.png"),]
testN3 <- testP3[which(testP3$Outcome == "NoDiamond.png"),]
#We also look at the NoDiamond outcome here, as that one is asked again

#the trial order this time around is different.


#X
X1F3 <- testF3[which(testF3$Trial == 2 | testF3$Trial == 5 | testF3$Trial == 8),]
avgX1F3 <- mean(X1F3$responseR2, na.rm = T)
X1D3 <- testD3[which(testD3$Trial == 1 | testD3$Trial == 4 | testD3$Trial == 7),]
avgX1D3 <- mean(X1D3$responseR2, na.rm = T)
X1N3 <- testN3[which(testN3$Trial == 3 | testN3$Trial == 6 | testN3$Trial == 9),]
avgX1N3 <- mean(X1N3$responseR2, na.rm = T)
X3F3 <- testF3[which(testF3$Trial == 11 | testF3$Trial == 14),]
avgX3F3 <- mean(X3F3$responseR2, na.rm = T)
X3D3 <- testD3[which(testD3$Trial == 10 | testD3$Trial == 13),]
avgX3D3 <- mean(X3D3$responseR2, na.rm = T)
X3N3 <- testN3[which(testN3$Trial == 12 | testN3$Trial == 15),]
avgX3N3 <- mean(X3N3$responseR2, na.rm = T)


#A
A1F3 <- testF3[which(testF3$Trial == 2),]
avgA1F3 <- mean(A1F3$responseR1, na.rm = T)
A1D3 <- testD3[which(testD3$Trial == 1),]
avgA1D3 <- mean(A1D3$responseR1, na.rm = T)
A1N3 <- testN3[which(testN3$Trial == 3),]
avgA1N3 <- mean(A1N3$responseR1, na.rm = T)
A3F3 <- testF3[which(testF3$Trial == 11),]
avgA3F3 <- mean(A3F3$responseR1, na.rm = T)
A3D3 <- testD3[which(testD3$Trial == 10),]
avgA3D3 <- mean(A3D3$responseR1, na.rm = T)
A3N3 <- testN3[which(testN3$Trial == 12),]
avgA3N3 <- mean(A3N3$responseR1, na.rm = T)

#B
B1F3 <- testF3[which(testF3$Trial == 5),]
avgB1F3 <- mean(B1F3$responseR1, na.rm = T)
B1D3 <- testD3[which(testD3$Trial == 4),]
avgB1D3 <- mean(B1D3$responseR1, na.rm = T)
B1N3 <- testN3[which(testN3$Trial == 6),]
avgB1N3 <- mean(B1N3$responseR1, na.rm = T)
B3F3 <- testF3[which(testF3$Trial == 14),]
avgB3F3 <- mean(B3F3$responseR1, na.rm = T)
B3D3 <- testD3[which(testD3$Trial == 13),]
avgB3D3 <- mean(B3D3$responseR1, na.rm = T)
B3N3 <- testN3[which(testN3$Trial == 15),]
avgB3N3 <- mean(B3N3$responseR1, na.rm = T)

#C
CF3 <- testF3[which(testF3$Trial == 8),]
avgCF3 <- mean(CF3$responseR1, na.rm = T)
CD3 <- testD3[which(testD3$Trial == 7),]
avgCD3 <- mean(CD3$responseR1, na.rm = T)
CN3 <- testN3[which(testN3$Trial == 9),]
avgCN3 <- mean(CN3$responseR1, na.rm = T)

Diamond3 <- c(avgA1D3, avgB1D3, avgX1D3, avgCD3, avgA3D3, avgB3D3, avgX3D3)
Fossil3 <- c(avgA1F3, avgB1F3, avgX1F3, avgCF3, avgA3F3, avgB3F3, avgX3F3)
NoDiamond3 <- c(avgA1N3, avgB1N3, avgX1N3, avgCN3, avgA3N3, avgB3N3, avgX3N3)
Phase3 <- data.frame(Cue, Diamond3, Fossil3, NoDiamond3)

Original <- c(ABl1, BBl1, XBl1, "NA", ABl3, BBl3, XBl3)
Phase3$Original <- as.numeric(Original)
Phase3
```
```{r}
#differences to the original stimuli in the training phase
t.test(A1D3$responseR1, train$responseR1[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = FALSE) #no diff
t.test(B1D3$responseR1, train$responseR2[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = FALSE) #no diff
t.test(X1D3$responseR2, train$responseR3[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = FALSE) #no diff
t.test(A3D3$responseR1, train$responseR1[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = FALSE) #no diff
t.test(B3D3$responseR1, train$responseR2[train$blockNr == "Block3"& train$Trial == 16], alternative = "two.sided", paired = FALSE) #no diff
t.test(X3D3$responseR2, train$responseR3[train$blockNr == "Block3"& train$Trial == 16], alternative = "two.sided", paired = FALSE) #no diff
#There are no significant differences between the scores to diamond in the test phase and the scores given in the original block. It seems as though people did notice the categories. 


#what happens if we see if there is a difference to the scores of A, B and X to allergic and those to no allergic?
t.test(A1D3$responseR1, A1N3$responseR1, alternative = "two.sided", paired = FALSE) #no diff
t.test(B1D3$responseR1, B1N3$responseR1, alternative = "two.sided", paired = FALSE) #no diff
t.test(X1D3$responseR2, X1N3$responseR2, alternative = "two.sided", paired = FALSE) #no diff
t.test(A3D3$responseR1, A3N3$responseR1, alternative = "two.sided", paired = FALSE) #no diff
t.test(B3D3$responseR1, B3N3$responseR1, alternative = "two.sided", paired = FALSE) #no diff
t.test(X3D3$responseR2, X3N3$responseR2, alternative = "two.sided", paired = FALSE) #no diff
#No differences here. That might indicate that people just were very not sure, as there isn't a clear higher score for a diamond outcome than a non diamond outcome
```


