---
title: "Experiment 1 T-tests"
author: "Sanne Poelstra"
date: "14/03/2021"
output:
  html_document:
    toc: true
    theme: united
---

```{r, include = FALSE}
rm(list=ls())
library(plotfunctions)
library("plotrix")
library("phonTools")
```

# Preparing the data
```{r, reading in the csv file}
d <- read.csv("Experiment1.csv", header = TRUE, sep = ',')
#This is quite a lot so I want to trim it somewhat, e.g. things such as font are not needed
dat <- d[, c("A", "A1", "A1_alt", "A2", "A3", "A3_alt", "B", "B1", "B1_alt", "B2", "B3", "B3_alt", "X", "X1", "X1_alt", "X2", "X3", "X3_alt", "C", "C_alt", "Outcome", "Stim1", "Stim2", "responseR1", "responseR2", "responseR3",  "block1", "block2", "block3", "average_response_time", "avg_rt", "NewAnswers", "Practice", "date_starttime", "jatosStudyResultId", "pos1X", "pos1Y", "pos2X", "pos2Y", "prolific_id", "response_time", "Cond", "Train_Test", "screen_availableHeight", "screen_availableWidth",  "timeout_occurred", "total_response_time", "Trial")]

#other things that would be interesting to look at later maybe: 
#> I also have the times that people were on the (text)screens
#> There are counters for each of the screens

head(dat)

###############
#now there were also some prolific IDs that were rejected, so I have to remove them
dat <- dat[which(dat$prolific_id != "5eef8aa4039a790817217ba3" & dat$prolific_id != "5eab2033f0b5cc0d9f44331d" & dat$prolific_id != "5f5624cfbb2be4a0571cb9ce" & dat$prolific_id != "60075182b660fb21ca5b3837" & dat$prolific_id != "5fabcdd6a5caa50491afce19" & dat$prolific_id != "5f93eb0c092fa01d2ed5da10" & dat$prolific_id != "5f6d9723b4a3d2212bd83eee" & dat$prolific_id != "5f6b36e1ab9578230dd425df"),]

#plus remove those that returned themselves!!
dat <- dat[which(dat$prolific_id != "601ddab3d1b8f21ea2f22865" & dat$prolific_id != "6040d72da487f5368a2eeddb" & dat$prolific_id != "5fd73d274ea4626dde59f11d" & dat$prolific_id != "5ccf6e4c222373001912f644" & dat$prolific_id != "5edb9139dc4bc502f26c4019" & dat$prolific_id != "6046740c46c42f05d552e99e" & dat$prolific_id != "5c93fd66503aea0001360bfd" & dat$prolific_id != "5f34d671952faa402de77cdc" & dat$prolific_id != "604c919f4e274caaf2502bdd" & dat$prolific_id != "5dbf4877f33f403e418eb9ac" & dat$prolific_id != "5f132e2f1e837c059737eda3" & dat$prolific_id != "5e52894c77e0502a16cb4354" & dat$prolific_id != "604ce30820ad61b5acbf037f" & dat$prolific_id != "5e8237edf80ed29537e1759b" & dat$prolific_id != "60300a6be9ee912613f17752" & dat$prolific_id != "5efd04a3b8abd1137b0ab607" & dat$prolific_id != "5f8afc0dd9375a1cc895ebe2" & dat$prolific_id != "5915bacd0a4b9d0001add6d5"),]

length(unique(dat$prolific_id))
#Note participants 5e739143d4934a023004b7fc experiment went a bit weird, she did 18 trials in the first block, 19 in the second, and the third block went fine
#Participant 5f9aba6600cdf11f1c9b915c had an extra practice run for some reason
```

```{r, warning = FALSE }
#As we don't know yet which condition was the first block, I'm going to have to assign a new column with that value
#blockNr depends on the value of block 1. If block 1 was 0 (internally 0 meant condition 0) and the condition of this current trial is 0, then we give this the value "block 1"

dat$blockNr <- ""
dat <- within(dat, blockNr[block1 == '0' & Cond == 0] <- 'Block1')
dat <- within(dat, blockNr[block1 == '1' & Cond == 50] <- 'Block1')
dat <- within(dat, blockNr[block1 == '2' & Cond == 100] <- 'Block1')
dat <- within(dat, blockNr[block2 == '0' & Cond == 0] <- 'Block2')
dat <- within(dat, blockNr[block2 == '1' & Cond == 50] <- 'Block2')
dat <- within(dat, blockNr[block2 == '2' & Cond == 100] <- 'Block2')
dat <- within(dat, blockNr[block3 == '0' & Cond == 0] <- 'Block3')
dat <- within(dat, blockNr[block3 == '1' & Cond == 50] <- 'Block3')
dat <- within(dat, blockNr[block3 == '2' & Cond == 100] <- 'Block3')

dat$CondFirstBlock <- ''
dat$CondSecondBlock <- ''
dat$CondThirdBlock <- '' 

dat$prolific_id <- as.factor(dat$prolific_id)

#to later compare the cues in the test phase to the condition they were originally asked in, we need another new column
#so for each participant, what condition was block 1? Save that in a row, what condition was block 3?
for(i in unique(dat$prolific_id)){
  dat <- within(dat, CondFirstBlock[prolific_id == i] <- Cond[prolific_id == i & blockNr == "Block1"])
  dat <- within(dat, CondSecondBlock[prolific_id == i] <- Cond[prolific_id == i & blockNr == "Block2"])
  dat <- within(dat, CondThirdBlock[prolific_id == i] <- Cond[prolific_id == i & blockNr == "Block3"])
} #HAAKJES

```

```{r, collect the data for the graphs}
#averages per condition, for X A and B
#responseR1 is always A, R2 is always B and R3 is always X

#train is the training phase. I want to make both a plot with 1's as answers removed, and one with all the answers, so I'll create two "train" dataframes
train1 <- dat[which(dat$Train_Test == "Train"),]
train <- dat[which(dat$Train_Test == "Train"),]

#Filter the 999 ones
train$responseR1[train$responseR1 == 999] <- NA
train$responseR2[train$responseR2 == 999] <- NA
train$responseR3[train$responseR3 == 999] <- NA

train1$responseR1[train1$responseR1 == 999] <- NA
train1$responseR2[train1$responseR2 == 999] <- NA
train1$responseR3[train1$responseR3 == 999] <- NA

train1$responseR1[train$responseR1 == 1] <- NA
train1$responseR2[train$responseR2 == 1] <- NA
train1$responseR3[train$responseR3 == 1] <- NA

#I need to relevel the data as otherwise it will level it as 0, 100, 50, which will plot wrong
train$Cond <- as.factor(train$Cond)
train$Cond <- factor(train$Cond, levels = c("0", "50", "100"))

train1$Cond <- as.factor(train1$Cond)
train1$Cond <- factor(train1$Cond, levels = c("0", "50", "100"))

a <- aggregate(list(train$responseR1, train$responseR2, train$responseR3), list(train$Cond), mean, na.rm = T)
b <- aggregate(list(train1$responseR1, train1$responseR2, train1$responseR3), list(train1$Cond), mean, na.rm = T)

colnames(a) <- c("Cond", "A", "B", "X")
colnames(b) <- c("Cond", "A", "B", "X")
head(a)
head(b)
```

```{r}
#over the 16 trials, for each of the conditions, get the average response for A, B and X
AllTrials <- aggregate(list(train$responseR1, train$responseR2, train$responseR3), list(train$Cond, train$Trial), mean, na.rm = T)
AllTrials1 <- aggregate(list(train1$responseR1, train1$responseR2, train1$responseR3), list(train1$Cond, train1$Trial), mean, na.rm = T)
colnames(AllTrials) <- c("Cond", "Trial", "A", "B", "X") 
colnames(AllTrials1) <- c("Cond", "Trial", "A", "B", "X")

#Then split this into the different conditions
Cond000 <- AllTrials[which(AllTrials$Cond==0),]
Cond050 <- AllTrials[which(AllTrials$Cond==50),]
Cond100 <- AllTrials[which(AllTrials$Cond==100),]

#This is then the one without 1's
Cond0001 <- AllTrials1[which(AllTrials1$Cond==0),]
Cond0501 <- AllTrials1[which(AllTrials1$Cond==50),]
Cond1001 <- AllTrials1[which(AllTrials1$Cond==100),]
```

## Diamond versus no Diamond trials

```{r}
#Calculating the average scores on the trials where "Diamond" was the outcome, and on trials where "No Diamond" was the outcome
#We would expect that the scores to the No Diamond would be lower on average
Diamond <- subset(train, train$Outcome == "Diamond.png")
NoDiamond <- subset(train, train$Outcome == "NoDiamond.png")

DiamondAvg <- aggregate(list(Diamond$responseR1, Diamond$responseR2, Diamond$responseR3), list(Diamond$Cond), mean, na.rm = T)
NoDiamondAvg <- aggregate(list(NoDiamond$responseR1, NoDiamond$responseR2, NoDiamond$responseR3), list(NoDiamond$Cond), mean, na.rm = T)
SE <- c(std.error(Diamond$responseR1[Diamond$Cond == "0"]), std.error(NoDiamond$responseR1[NoDiamond$Cond == "0"]), std.error(Diamond$responseR2[Diamond$Cond == "0"]), std.error(NoDiamond$responseR2[NoDiamond$Cond == "0"]), std.error(Diamond$responseR3[Diamond$Cond == "0"]), std.error(NoDiamond$responseR3[NoDiamond$Cond == "0"]),  std.error(Diamond$responseR1[Diamond$Cond == "50"]), std.error(NoDiamond$responseR1[NoDiamond$Cond == "50"]), std.error(Diamond$responseR2[Diamond$Cond == "50"]), std.error(NoDiamond$responseR2[NoDiamond$Cond == "50"]), std.error(Diamond$responseR3[Diamond$Cond == "50"]), std.error(NoDiamond$responseR3[NoDiamond$Cond == "50"]),  std.error(Diamond$responseR1[Diamond$Cond == "100"]), std.error(NoDiamond$responseR1[NoDiamond$Cond == "100"]), std.error(Diamond$responseR2[Diamond$Cond == "100"]), std.error(NoDiamond$responseR2[NoDiamond$Cond == "100"]), std.error(Diamond$responseR3[Diamond$Cond == "100"]), std.error(NoDiamond$responseR3[NoDiamond$Cond == "100"]))
colnames(DiamondAvg) <- c("Cond", "A", "B", "X")
colnames(NoDiamondAvg) <- c("Cond", "A", "B", "X")

DiamondAvg
NoDiamondAvg
```

## Aggregating the data over participants
<br/> For a t.test you need 1 datapoint per participant
```{r}
Diamond <- aggregate(list(Diamond$responseR1, Diamond$responseR2, Diamond$responseR3), by = list(Diamond$prolific_id, Diamond$Cond), mean, na.rm = T)
names(Diamond) <- c("Participant", "Cond", "responseR1", "responseR2", "responseR3")

NoDiamond <- aggregate(list(NoDiamond$responseR1, NoDiamond$responseR2, NoDiamond$responseR3), by = list(NoDiamond$prolific_id, NoDiamond$Cond), mean, na.rm = T)
names(NoDiamond) <- c("Participant", "Cond", "responseR1", "responseR2", "responseR3")

# compute the difference
d <- Diamond$responseR1[Diamond$Cond == "0"] - NoDiamond$responseR1[NoDiamond$Cond == "0"]
shapiro.test(d) # => p-value = 0.001
d <- Diamond$responseR2[Diamond$Cond == "0"] - NoDiamond$responseR2[NoDiamond$Cond == "0"]
shapiro.test(d) # => p-value < 0.001
d <- Diamond$responseR3[Diamond$Cond == "0"] - NoDiamond$responseR3[NoDiamond$Cond == "0"]
shapiro.test(d) # => p-value < 0.001

d <- Diamond$responseR1[Diamond$Cond == "50"] - NoDiamond$responseR1[NoDiamond$Cond == "50"]        #NOT NORMALLY DIST
shapiro.test(d) # => p-value = 0.22
d <- Diamond$responseR2[Diamond$Cond == "50"] - NoDiamond$responseR2[NoDiamond$Cond == "50"]
shapiro.test(d) # => p-value = 0.003
d <- Diamond$responseR3[Diamond$Cond == "50"] - NoDiamond$responseR3[NoDiamond$Cond == "50"]
shapiro.test(d) # => p-value < 0.001

d <- Diamond$responseR1[Diamond$Cond == "100"] - NoDiamond$responseR1[NoDiamond$Cond == "100"]
shapiro.test(d) # => p-value < 0.001
d <- Diamond$responseR2[Diamond$Cond == "100"] - NoDiamond$responseR2[NoDiamond$Cond == "100"]
shapiro.test(d) # => p-value < 0.001
d <- Diamond$responseR3[Diamond$Cond == "100"] - NoDiamond$responseR3[NoDiamond$Cond == "100"]
shapiro.test(d) # => p-value = 0.01
```

```{r}
#but now we have a problem, as there are two different groups 
t.test(Diamond$responseR1[Diamond$Cond == "0"], NoDiamond$responseR1[NoDiamond$Cond == "0"], alternative = "two.sided", paired = T) #sign, diamond higher than not diamond
t.test(Diamond$responseR2[Diamond$Cond == "0"], NoDiamond$responseR2[NoDiamond$Cond == "0"], alternative = "two.sided", paired = T) #niet sign
t.test(Diamond$responseR3[Diamond$Cond == "0"], NoDiamond$responseR3[NoDiamond$Cond == "0"], alternative = "two.sided", paired = T) #sign, diamond higher than not diamond

t.test(Diamond$responseR1[Diamond$Cond == "50"], NoDiamond$responseR1[NoDiamond$Cond == "50"], alternative = "two.sided", paired = T) #sign, diamond higher than not diamond
t.test(Diamond$responseR2[Diamond$Cond == "50"], NoDiamond$responseR2[NoDiamond$Cond == "50"], alternative = "two.sided", paired = T) #not sign
t.test(Diamond$responseR3[Diamond$Cond == "50"], NoDiamond$responseR3[NoDiamond$Cond == "50"], alternative = "two.sided", paired = T) #sign, diamond higher than not diamond

t.test(Diamond$responseR1[Diamond$Cond == "100"], NoDiamond$responseR1[NoDiamond$Cond == "100"], alternative = "two.sided", paired = T) #sign, diamond higher than not diamond
t.test(Diamond$responseR2[Diamond$Cond == "100"], NoDiamond$responseR2[NoDiamond$Cond == "100"], alternative = "two.sided", paired = T) #not sign
t.test(Diamond$responseR3[Diamond$Cond == "100"], NoDiamond$responseR3[NoDiamond$Cond == "100"], alternative = "two.sided", paired = T) #sign, diamond higher than not diamond
```

<br/> 
<br/>
These t-test show exactly what we would expect. The diamond trials are always scored higher than the no diamond trials. That is except for B. This makes sense though, because, except for the 50-50 condition, B predicts an diamond outcome a lot less than the others. So here we would expect that people will start to score B lower overall, even on the trials where it does predict an allergic reaction. <br/>

```{r}
p <- c(0.0158, 0.08852, 0.0262, 3.045e-06, 0.4201, 6.239e-05, 8.636e-06, 0.7994, 0.003404)
p.adjust(p, method = "holm", n = length(p)) #holm is a more lenient way
#p.adjust(p, method = "bonferroni", n = length(p))

#not sign, not, not, yes, not, yes, yes, not, yes

``` 
So this changes things. Now 5/9 show no difference, while 4/9 do. 

# Test phase
```{r}
#First getting the test phase data 
test <- dat[which(dat$Train_Test == "Test"),] 
test$responseR1[test$responseR1 == 999] <- NA
test$responseR2[test$responseR2 == 999] <- NA
test$responseR3[test$responseR3 == 999] <- NA

#And also splitting them into the different phases
testP1 <- test[which(test$Cond == "Phase1"),]
testP2 <- test[which(test$Cond == "Phase2"),]
testP3 <- test[which(test$Cond == "Phase3"),]
testP12 <- test[which(test$Cond == "Phase1" | test$Cond == "Phase2"),]
```

## Phase 1
<br/> This phase was in the same order for each participant. At first the cues from the first block were seen, then a new cue (together with X of the first block) and then those of the third block were seen. This time participants were asked how likely they thought these items would lead to outcome Y, with Y being either a diamond (which they've seen before) or a fossil (a new outcome)

### Creating and preparing the data
```{r}
#Phase 1

#I want to look at the outcome to fossil and that to diamond
testF <- testP1[which(testP1$Outcome == "Fossil.png"),]
testD <- testP1[which(testP1$Outcome == "Diamond.png"),]

#Now I want the average scores for A B and X for each of these outcomes, but also specifically A1, B1 etc. Therefore I will have to look at specific responses to trials. Therefore aggregate isn't very useful to use here.

#X
X1F <- testF[which(testF$Trial == 2 | testF$Trial == 4 | testF$Trial == 6),]
avgX1F <- mean(X1F$responseR2, na.rm = T)
X1D <- testD[which(testD$Trial == 1 | testD$Trial == 3 | testD$Trial == 5),]
avgX1D <- mean(X1D$responseR2, na.rm = T)
X3F <- testF[which(testF$Trial == 8 | testF$Trial == 10),]
avgX3F <- mean(X3F$responseR2, na.rm = T)
X3D <- testD[which(testD$Trial == 7 | testD$Trial == 9),]
avgX3D <- mean(X3D$responseR2, na.rm = T)

#A
A1F <- testF[which(testF$Trial == 2),]
avgA1F <- mean(A1F$responseR1, na.rm = T)
A1D <- testD[which(testD$Trial == 1),]
avgA1D <- mean(A1D$responseR1, na.rm = T)

A3F <- testF[which(testF$Trial == 8),]
avgA3F <- mean(A3F$responseR1, na.rm = T)
A3D <- testD[which(testD$Trial == 7),]
avgA3D <- mean(A3D$responseR1, na.rm = T)

#B
B1F <- testF[which(testF$Trial == 4),]
avgB1F <- mean(B1F$responseR1, na.rm = T)
B1D <- testD[which(testD$Trial == 3),]
avgB1D <- mean(B1D$responseR1, na.rm = T)

B3F <- testF[which(testF$Trial == 10),]
avgB3F <- mean(B3F$responseR1, na.rm = T)
B3D <- testD[which(testD$Trial == 9),]
avgB3D <- mean(B3D$responseR1, na.rm = T)

#C
CF <- testF[which(testF$Trial == 6),]
avgCF <- mean(CF$responseR1, na.rm = T)
CD <- testD[which(testD$Trial == 5),]
avgCD <- mean(CD$responseR1, na.rm = T)


Cue <- c("A1", "B1", "X1", "C", "A3", "B3", "X3")
Diamond <- c(avgA1D, avgB1D, avgX1D, avgCD, avgA3D, avgB3D, avgX3D)
Fossil <- c(avgA1F, avgB1F, avgX1F, avgCF, avgA3F, avgB3F, avgX3F)
Phase1 <- data.frame(Cue, Diamond, Fossil)
Phase1

```
<br/>
So there are some differences between scoring to diamond (seems a lot higher, expect for C) and Fossil. The thing here is though that these are all categories collapsed. Later we will split those categories and see what happens then. <br />
Now I'll get the scores over the entire block.

```{r}
#now that we know what was asked when in the training phase 

ABl1 <- mean(train$responseR1[train$blockNr == "Block1" & train$Trial == 16], na.rm = T)
BBl1 <- mean(train$responseR2[train$blockNr == "Block1" & train$Trial == 16], na.rm = T)
XBl1 <- mean(train$responseR3[train$blockNr == "Block1" & train$Trial == 16], na.rm = T)

ABl3 <- mean(train$responseR1[train$blockNr == "Block3" & train$Trial == 16], na.rm = T)
BBl3 <- mean(train$responseR2[train$blockNr == "Block3" & train$Trial == 16], na.rm = T)
XBl3 <- mean(train$responseR3[train$blockNr == "Block3" & train$Trial == 16], na.rm = T)

Cues <- c("A1", "B1", "X1", "A3", "B3", "X3")
Mean <- c(ABl1, BBl1, XBl1, ABl3, BBl3, XBl3)
TrainAvgBl1_3 <- data.frame(Cues, Mean) 
TrainAvgBl1_3

Original <- c(ABl1, BBl1, XBl1, "NA", ABl3, BBl3, XBl3)
Phase1$Original <- as.numeric(Original)
Phase1

```
<br/> Here we can see the differences in scores to diamond in the test phase (1), fossil (test phase 1) and the original scores to A, B and X in block 1 and 3. This is averaged over all conditions. We will now perform t-tests to see if there is a difference between these values.

#### Conditions taken together
 <br/> Note that trial 16 is taken for B and X as that is the last time BX is shown, but 15 is the last time AX is shown, so 15 is used for A cues
 
```{r}
#Technically speaking for A and B there is already 1 datapoint per participant, but for safety reasons I'll still aggregate them!
A1D <- aggregate(list(A1D$responseR1), by = list(A1D$prolific_id), mean, na.rm = T)
names(A1D) <- c("Participant", "responseR1")
B1D <- aggregate(list(B1D$responseR1), by = list(B1D$prolific_id), mean, na.rm = T)
names(B1D) <- c("Participant", "responseR1")
X1D <- aggregate(list(X1D$responseR2), by = list(X1D$prolific_id), mean, na.rm = T)
names(X1D) <- c("Participant", "responseR2")

A3D <- aggregate(list(A3D$responseR1), by = list(A3D$prolific_id), mean, na.rm = T)
names(A3D) <- c("Participant", "responseR1")
B3D <- aggregate(list(B3D$responseR1), by = list(B3D$prolific_id), mean, na.rm = T)
names(B3D) <- c("Participant", "responseR1")
X3D <- aggregate(list(X3D$responseR2), by = list(X3D$prolific_id), mean, na.rm = T)
names(X3D) <- c("Participant", "responseR2")

CD <- aggregate(list(CD$responseR1), by = list(CD$prolific_id), mean, na.rm = T)
names(CD) <- c("Participant", "responseR1")


A1F <- aggregate(list(A1F$responseR1), by = list(A1F$prolific_id), mean, na.rm = T)
names(A1F) <- c("Participant", "responseR1")
B1F <- aggregate(list(B1F$responseR1), by = list(B1F$prolific_id), mean, na.rm = T)
names(B1F) <- c("Participant", "responseR1")
X1F <- aggregate(list(X1F$responseR2), by = list(X1F$prolific_id), mean, na.rm = T)
names(X1F) <- c("Participant", "responseR2")

A3F <- aggregate(list(A3F$responseR1), by = list(A3F$prolific_id), mean, na.rm = T)
names(A3F) <- c("Participant", "responseR1")
B3F <- aggregate(list(B3F$responseR1), by = list(B3F$prolific_id), mean, na.rm = T)
names(B3F) <- c("Participant", "responseR1")
X3F <- aggregate(list(X3F$responseR2), by = list(X3F$prolific_id), mean, na.rm = T)
names(X3F) <- c("Participant", "responseR2")

CF <- aggregate(list(CF$responseR1), by = list(CF$prolific_id), mean, na.rm = T)
names(CF) <- c("Participant", "responseR1")

d <- A1D$responseR1 - train$responseR1[train$blockNr == "Block1" & train$Trial == 15] #NOT NORMALLY DIST
shapiro.test(d) # p = 0.35
d <- B1D$responseR1 - train$responseR2[train$blockNr == "Block1" & train$Trial == 16] 
shapiro.test(d) # p = 0.02
d <- X1D$responseR2 - train$responseR3[train$blockNr == "Block1" & train$Trial == 16] 
shapiro.test(d) # p = 0.01

d <- A3D$responseR1 - train$responseR1[train$blockNr == "Block3" & train$Trial == 15] #NOT NORMALLY DIST
shapiro.test(d) # p = 0.27
d <- B3D$responseR1 - train$responseR2[train$blockNr == "Block3" & train$Trial == 16] #NOT NORMALLY DIST
shapiro.test(d) # p = 0.31
d <- X3D$responseR2 - train$responseR3[train$blockNr == "Block3" & train$Trial == 16] #NOT NORMALLY DIST
shapiro.test(d) # p = 0.6515
```

#### Difference training and test phase 
```{r}
#for just the last block to compare it to
#1) Are there significant differences between A, B and X when asked in their original block 1 and in the test phase
t.test(A1D$responseR1, train$responseR1[train$blockNr == "Block1" & train$Trial == 15], alternative = "two.sided", paired = T) #sign diff, decrease *
t.test(B1D$responseR1, train$responseR2[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = T) #sign diff, increase
t.test(X1D$responseR2, train$responseR3[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff


#2) Are there sign differences between A, B and X when asked in block 3 and in the test phase
wilcox.test(A3D$responseR1, train$responseR1[train$blockNr == "Block3" & train$Trial == 15], alternative = "two.sided", paired = T) #no diff *
wilcox.test(B3D$responseR1, train$responseR2[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff
wilcox.test(X3D$responseR2, train$responseR3[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff

#there is a significant difference for 2/3 cues in the first block. This would be according to the van hamme wasserman paper, and as there are less differences in the third block, this would still be in line with van hamme and wasserman. NO LONGER TRUE

#What we now have is a all the things of the first block differing, and the second block not. But there is an increase and now also a decrease in A
```

```{r}
p <- c(0.0005357, 0.02369, 0.08272, 0.2611, 0.7253, 0.09085)
p.adjust(p, method = "holm", n = length(p))
#yes, no, no, no, no, no
```

#### Difference C and rest of the cues
```{r}
d <- CD$responseR1 - A1D$responseR1 #NOT NORMALLY DIST
shapiro.test(d) # p = 0.29
d <- CD$responseR1 - B1D$responseR1 #NOT NORMALLY DIST
shapiro.test(d) # p = 0.31
d <- CD$responseR1 - X1D$responseR2 #NOT NORMALLY DIST
shapiro.test(d) # p = 0.37

d <- CD$responseR1 - A3D$responseR1 
shapiro.test(d) # p = 0.04
d <- CD$responseR1 - B3D$responseR1 #NOT NORMALLY DIST
shapiro.test(d) # p = 0.08
d <- CD$responseR1 - X3D$responseR2 #NOT NORMALLY DIST
shapiro.test(d) # p = 0.07

```


```{r}
#3) Is there a sign difference between the C value and that of A B and X in the test phase 
wilcox.test(CD$responseR1, A1D$responseR1, alternative = "two.sided", paired = T) #no diff
wilcox.test(CD$responseR1, B1D$responseR1, alternative = "two.sided", paired = T) #diff lower C
wilcox.test(CD$responseR1, X1D$responseR2, alternative = "two.sided", paired = T) #diff lower C

wilcox.test(CD$responseR1, A3D$responseR1, alternative = "two.sided", paired = T) #diff, lower C
wilcox.test(CD$responseR1, B3D$responseR1, alternative = "two.sided", paired = T) #no sign diff
wilcox.test(CD$responseR1, X3D$responseR2, alternative = "two.sided", paired = F) #diff, lower C
```

```{r}
p <- c(0.09145, 0.004605, 0.0007185, 2.575e-05, 0.201, 0.001441)
p.adjust(p, method = "holm", n = length(p))
#no, yes, yes, yes, no, yes
```

#### Difference fossil and Diamond

```{r}
d <- A1D$responseR1 - A1F$responseR1
shapiro.test(d) # p = 0.02
d <- B1D$responseR1 - B1F$responseR1
shapiro.test(d) # p = 0.01
d <- X1D$responseR2 - X1F$responseR2
shapiro.test(d) # p = 0.03
d <- CD$responseR1 - CF$responseR1
shapiro.test(d) # p < 000.1
d <- A3D$responseR1 - A3F$responseR1
shapiro.test(d) # p = 0.006
d <- B3D$responseR1 - B3F$responseR1
shapiro.test(d) # p = 0.04
d <- X3D$responseR2 - X3F$responseR2
shapiro.test(d) # p = 0.01
```

```{r}
#4) Is there a difference between the ratings to fossil and those to diamond?
t.test(A1D$responseR1, A1F$responseR1, alternative = "two.sided", paired = T) #not sign
t.test(B1D$responseR1, B1F$responseR1, alternative = "two.sided", paired = T) #sign, lower score on the fossil than on the diamond
t.test(X1D$responseR2, X1F$responseR2, alternative = "two.sided", paired = T) #sign, lower score on the fossil than on the diamond
t.test(CD$responseR1, CF$responseR1, alternative = "two.sided", paired = T)   #no sign (makes sense! The cue is new)
t.test(A3D$responseR1, A3F$responseR1, alternative = "two.sided", paired = T) #sign, lower score on the fossil than on the diamond
t.test(B3D$responseR1, B3F$responseR1, alternative = "two.sided", paired = T) #sign, fossil higher than diamond)
t.test(X3D$responseR2, X3F$responseR2, alternative = "two.sided", paired = T) #not sign
```
<br/> Splitting over conditions will be done for 1 and 2 combined! As that will be the main analysis anyways

```{r}
p <- c(0.1232 , 0.0005893, 0.02704, 0.5681, 0.0007541, 0.0481, 0.4268)
p.adjust(p, method = "holm", n = length(p))
#no, yes, no, no, yes, no, no
```


## Phase 2
<br/>
In this phase participants saw the same stimuli as in Phase 1, but now in random order. We want to caclulate the average values of A, B and X to allergic and fever and see if they differ from those of Phase 1 (ideally they shouldnt).
```{r}
#Phase 2

#while the trials are in a different order this time around, Trial was a variable given to the _row_ in the table. So in order you will also see that it was "trials 9 then 4 then 8 for example.

#So we basically do the same as before but now I have to rename some things, because I still need stuff like X1F to compare with in a t.test.

testF2 <- testP2[which(testP2$Outcome == "Fossil.png"),]
testD2 <- testP2[which(testP2$Outcome == "Diamond.png"),]

#Now I want the average scores for A B and X for each of these outcomes, but also specifically A1, B1 etc. Therefore I will have to look at specific responses to trials. Therefore aggregate isn't very useful to use here.

#X
X1F2 <- testF2[which(testF2$Trial == 2 | testF2$Trial == 4 | testF2$Trial == 6),]
avgX1F2 <- mean(X1F2$responseR2, na.rm = T)
X1D2 <- testD2[which(testD2$Trial == 1 | testD2$Trial == 3 | testD2$Trial == 5),]
avgX1D2 <- mean(X1D2$responseR2, na.rm = T)
X3F2 <- testF2[which(testF2$Trial == 8 | testF2$Trial == 10),]
avgX3F2 <- mean(X3F2$responseR2, na.rm = T)
X3D2 <- testD2[which(testD2$Trial == 7 | testD2$Trial == 9),]
avgX3D2 <- mean(X3D2$responseR2, na.rm = T)

#A
A1F2 <- testF2[which(testF2$Trial == 2),]
avgA1F2 <- mean(A1F2$responseR1, na.rm = T)
A1D2 <- testD2[which(testD2$Trial == 1),]
avgA1D2 <- mean(A1D2$responseR1, na.rm = T)
A3F2 <- testF2[which(testF2$Trial == 8),]
avgA3F2 <- mean(A3F2$responseR1, na.rm = T)
A3D2 <- testD2[which(testD2$Trial == 7),]
avgA3D2 <- mean(A3D2$responseR1, na.rm = T)

#B
B1F2 <- testF2[which(testF2$Trial == 4),]
avgB1F2 <- mean(B1F2$responseR1, na.rm = T)
B1D2 <- testD2[which(testD2$Trial == 3),]
avgB1D2 <- mean(B1D2$responseR1, na.rm = T)

B3F2 <- testF2[which(testF2$Trial == 10),]
avgB3F2 <- mean(B3F2$responseR1, na.rm = T)
B3D2 <- testD2[which(testD2$Trial == 9),]
avgB3D2 <- mean(B3D2$responseR1, na.rm = T)

#C
CF2 <- testF2[which(testF2$Trial == 6),]
avgCF2 <- mean(CF2$responseR1, na.rm = T)
CD2 <- testD2[which(testD2$Trial == 5),]
avgCD2 <- mean(CD2$responseR1, na.rm = T)


Cue <- c("A1", "B1", "X1", "C", "A3", "B3", "X3")
Diamond2 <- c(avgA1D2, avgB1D2, avgX1D2, avgCD2, avgA3D2, avgB3D2, avgX3D2)
Fossil2 <- c(avgA1F2, avgB1F2, avgX1F2, avgCF2, avgA3F2, avgB3F2, avgX3F2)
Phase2 <- data.frame(Cue, Diamond2, Fossil2)
Phase2
Phase1_2 <- data.frame(Cue, Diamond, Fossil, Diamond2, Fossil2)
Phase1_2

```
<br/> From first glace there don't seem to be big differences, except maybe for A3's score to fossil. Let's see

```{r}
A1D2 <- aggregate(list(A1D2$responseR1), by = list(A1D2$prolific_id), mean, na.rm = T)
names(A1D2) <- c("Participant", "responseR1")
B1D2 <- aggregate(list(B1D2$responseR1), by = list(B1D2$prolific_id), mean, na.rm = T)
names(B1D2) <- c("Participant", "responseR1")
X1D2 <- aggregate(list(X1D2$responseR2), by = list(X1D2$prolific_id), mean, na.rm = T)
names(X1D2) <- c("Participant", "responseR2")

A3D2 <- aggregate(list(A3D2$responseR1), by = list(A3D2$prolific_id), mean, na.rm = T)
names(A3D2) <- c("Participant", "responseR1")
B3D2 <- aggregate(list(B3D2$responseR1), by = list(B3D2$prolific_id), mean, na.rm = T)
names(B3D2) <- c("Participant", "responseR1")
X3D2 <- aggregate(list(X3D2$responseR2), by = list(X3D2$prolific_id), mean, na.rm = T)
names(X3D2) <- c("Participant", "responseR2")

A1F2 <- aggregate(list(A1F2$responseR1), by = list(A1F2$prolific_id), mean, na.rm = T)
names(A1F2) <- c("Participant", "responseR1")
B1F2 <- aggregate(list(B1F2$responseR1), by = list(B1F2$prolific_id), mean, na.rm = T)
names(B1F2) <- c("Participant", "responseR1")
X1F2 <- aggregate(list(X1F2$responseR2), by = list(X1F2$prolific_id), mean, na.rm = T)
names(X1F2) <- c("Participant", "responseR2")

A3F2 <- aggregate(list(A3F2$responseR1), by = list(A3F2$prolific_id), mean, na.rm = T)
names(A3F2) <- c("Participant", "responseR1")
B3F2 <- aggregate(list(B3F2$responseR1), by = list(B3F2$prolific_id), mean, na.rm = T)
names(B3F2) <- c("Participant", "responseR1")
X3F2 <- aggregate(list(X3F2$responseR2), by = list(X3F2$prolific_id), mean, na.rm = T)
names(X3F2) <- c("Participant", "responseR2")

CD2 <- aggregate(list(CD2$responseR1), by = list(CD2$prolific_id), mean, na.rm =T)
names(CD2) <- c("Participant", "responseR1")
CF2 <- aggregate(list(CF2$responseR1), by = list(CF2$prolific_id), mean, na.rm =T)
names(CF2) <- c("Participant", "responseR1")

d <- A1D$responseR1 - A1D2$responseR1
shapiro.test(d) # p = 0.003
d <- B1D$responseR1 - B1D2$responseR1
shapiro.test(d) # p = 0.003
d <- X1D$responseR2 - X1D2$responseR2
shapiro.test(d) # p = 0.02
d <- CD$responseR1 - CD2$responseR1
shapiro.test(d) # p < 0.001
d <- A3D$responseR1 - A3D2$responseR1
shapiro.test(d) # p < 0.001
d <- B3D$responseR1 - B3D2$responseR1
shapiro.test(d) # p < 0.001
d <- X3D$responseR2 - X3D2$responseR2
shapiro.test(d) # p < 0.001

d <- A1F$responseR1 - A1F2$responseR1
shapiro.test(d) # p = 0.03
d <- B1F$responseR1 - B1F2$responseR1
shapiro.test(d) # p = 0.001
d <- X1F$responseR2 - X1F2$responseR2 #NOT NORM DIST
shapiro.test(d) # p = 0.22
d <- CF$responseR1 - CF2$responseR1
shapiro.test(d) # p < 0.001
d <- A3F$responseR1 - A3F2$responseR1
shapiro.test(d) # p < 0.001
d <- B3F$responseR1 - B3F2$responseR1
shapiro.test(d) # p < 0.001
d <- X3F$responseR2 - X3F2$responseR2
shapiro.test(d) # p = 0.002




```


```{r}
#All no diff, so there is no difference between the scores in Phase 2 and Phase 1 to Diamond
t.test(A1D$responseR1, A1D2$responseR1, alternative = "two.sided", paired = T)
t.test(B1D$responseR1, B1D2$responseR1, alternative = "two.sided", paired = T)
t.test(X1D$responseR2, X1D2$responseR2, alternative = "two.sided", paired = T)
t.test(CD$responseR1, CD2$responseR1, alternative = "two.sided", paired = T)
t.test(A3D$responseR1, A3D2$responseR1, alternative = "two.sided", paired = T)
t.test(B3D$responseR1, B3D2$responseR1, alternative = "two.sided", paired = T)
t.test(X3D$responseR2, X3D2$responseR2, alternative = "two.sided", paired = T)

#all no diff too! So Phase 1 and 2 also don't differ in their scores to Fossil.
t.test(A1F$responseR1, A1F2$responseR1, alternative = "two.sided", paired = T)
t.test(B1F$responseR1, B1F2$responseR1, alternative = "two.sided", paired = T) #DIFF (not with unpaired, but with this one it is a diff)
t.test(X1F$responseR2, X1F2$responseR2, alternative = "two.sided", paired = T)
t.test(CF$responseR1, CF2$responseR1, alternative = "two.sided", paired = T)
t.test(A3F$responseR1, A3F2$responseR1, alternative = "two.sided", paired = T) #DIFF
t.test(B3F$responseR1, B3F2$responseR1, alternative = "two.sided", paired = T)
t.test(X3F$responseR2, X3F2$responseR2, alternative = "two.sided", paired = T)
```
```{r}
p <- c(0.8729 , 0.5903, 0.284, 0.5628, 0.5038, 0.9137, 0.8107)
p.adjust(p, method = "holm", n = length(p))
#no for all

p <- c(0.2137 , 0.01847, 1, 0.8019, 0.0459, 0.5723, 0.2308)
p.adjust(p, method = "holm", n = length(p))
#no for all
```

## Phase 1 and 2 combined into one dataset
```{r}
testF12 <- testP12[which(testP12$Outcome == "Fossil.png"),]
testD12 <- testP12[which(testP12$Outcome == "Diamond.png"),]

#X
X1F12 <- testF12[which(testF12$Trial == 2 | testF12$Trial == 4 | testF12$Trial == 6),]
avgX1F12 <- mean(X1F12$responseR2, na.rm = T)
X1D12 <- testD12[which(testD12$Trial == 1 | testD12$Trial == 3 | testD12$Trial == 5),]
avgX1D12 <- mean(X1D12$responseR2, na.rm = T)
X3F12 <- testF12[which(testF12$Trial == 8 | testF12$Trial == 10),]
avgX3F12 <- mean(X3F12$responseR2, na.rm = T)
X3D12 <- testD12[which(testD12$Trial == 7 | testD12$Trial == 9),]
avgX3D12 <- mean(X3D12$responseR2, na.rm = T)

#A
A1F12 <- testF12[which(testF12$Trial == 2),]
avgA1F12 <- mean(A1F12$responseR1, na.rm = T)
A1D12 <- testD12[which(testD12$Trial == 1),]
avgA1D12 <- mean(A1D12$responseR1, na.rm = T)

A3F12 <- testF12[which(testF12$Trial == 8),]
avgA3F12 <- mean(A3F12$responseR1, na.rm = T)
A3D12 <- testD12[which(testD12$Trial == 7),]
avgA3D12 <- mean(A3D12$responseR1, na.rm = T)

#B
B1F12 <- testF12[which(testF12$Trial == 4),]
avgB1F12 <- mean(B1F12$responseR1, na.rm = T)
B1D12 <- testD12[which(testD12$Trial == 3),]
avgB1D12 <- mean(B1D12$responseR1, na.rm = T)

B3F12 <- testF12[which(testF12$Trial == 10),]
avgB3F12 <- mean(B3F12$responseR1, na.rm = T)
B3D12 <- testD12[which(testD12$Trial == 9),]
avgB3D12 <- mean(B3D12$responseR1, na.rm = T)

#C
CF12 <- testF12[which(testF12$Trial == 6),]
avgCF12 <- mean(CF12$responseR1, na.rm = T)
CD12 <- testD12[which(testD12$Trial == 5),]
avgCD12 <- mean(CD12$responseR1, na.rm = T)

ABl1 <- mean(train$responseR1[train$blockNr == "Block1" & train$Trial == 15], na.rm = T)
BBl1 <- mean(train$responseR2[train$blockNr == "Block1" & train$Trial == 16], na.rm = T)
XBl1 <- mean(train$responseR3[train$blockNr == "Block1" & train$Trial == 16], na.rm = T)

ABl3 <- mean(train$responseR1[train$blockNr == "Block3" & train$Trial == 15], na.rm = T)
BBl3 <- mean(train$responseR2[train$blockNr == "Block3" & train$Trial == 16], na.rm = T)
XBl3 <- mean(train$responseR3[train$blockNr == "Block3" & train$Trial == 16], na.rm = T)


Cue <- c("A1", "B1", "X1", "C", "A3", "B3", "X3")
Diamond12 <- c(avgA1D12, avgB1D12, avgX1D12, avgCD12, avgA3D12, avgB3D12, avgX3D12)
Fossil12 <- c(avgA1F12, avgB1F12, avgX1F12, avgCF12, avgA3F12, avgB3F12, avgX3F12)
Original <- c(ABl1, BBl1, XBl1, "NA", ABl3, BBl3, XBl3)
Phase12 <- data.frame(Cue, Diamond12, Fossil12, Original)
Phase12
```


```{r}
A1D12 <- aggregate(list(A1D12$responseR1), by = list(A1D12$prolific_id), mean, na.rm = T)
names(A1D12) <- c("Participant", "responseR1")
B1D12 <- aggregate(list(B1D12$responseR1), by = list(B1D12$prolific_id), mean, na.rm = T)
names(B1D12) <- c("Participant", "responseR1")
X1D12 <- aggregate(list(X1D12$responseR2), by = list(X1D12$prolific_id), mean, na.rm = T)
names(X1D12) <- c("Participant", "responseR2")

A3D12 <- aggregate(list(A3D12$responseR1), by = list(A3D12$prolific_id), mean, na.rm = T)
names(A3D12) <- c("Participant", "responseR1")
B3D12 <- aggregate(list(B3D12$responseR1), by = list(B3D12$prolific_id), mean, na.rm = T)
names(B3D12) <- c("Participant", "responseR1")
X3D12 <- aggregate(list(X3D12$responseR2), by = list(X3D12$prolific_id), mean, na.rm = T)
names(X3D12) <- c("Participant", "responseR2")

A1F12 <- aggregate(list(A1F12$responseR1), by = list(A1F12$prolific_id), mean, na.rm = T)
names(A1F12) <- c("Participant", "responseR1")
B1F12 <- aggregate(list(B1F12$responseR1), by = list(B1F12$prolific_id), mean, na.rm = T)
names(B1F12) <- c("Participant", "responseR1")
X1F12 <- aggregate(list(X1F12$responseR2), by = list(X1F12$prolific_id), mean, na.rm = T)
names(X1F12) <- c("Participant", "responseR2")

A3F12 <- aggregate(list(A3F12$responseR1), by = list(A3F12$prolific_id), mean, na.rm = T)
names(A3F12) <- c("Participant", "responseR1")
B3F12 <- aggregate(list(B3F12$responseR1), by = list(B3F12$prolific_id), mean, na.rm = T)
names(B3F12) <- c("Participant", "responseR1")
X3F12 <- aggregate(list(X3F12$responseR2), by = list(X3F12$prolific_id), mean, na.rm = T)
names(X3F12) <- c("Participant", "responseR2")

CD12 <- aggregate(list(CD12$responseR1), by = list(CD12$prolific_id), mean, na.rm =T)
names(CD12) <- c("Participant", "responseR1")
CF12 <- aggregate(list(CF12$responseR1), by = list(CF12$prolific_id), mean, na.rm =T)
names(CF12) <- c("Participant", "responseR1")

d <- A1D12$responseR1 - train$responseR1[train$blockNr == "Block1" & train$Trial == 15] #NOT NORM DIST
shapiro.test(d) # p = 0.25
d <- B1D12$responseR1 - train$responseR2[train$blockNr == "Block1" & train$Trial == 16] #NOT NORM DIST
shapiro.test(d) #p = 0.06
d <- X1D12$responseR2 - train$responseR3[train$blockNr == "Block1" & train$Trial == 16]
shapiro.test(d) #p = 0.04
 
d <- A3D12$responseR1 - train$responseR1[train$blockNr == "Block3" & train$Trial == 15] #NOT NORM DIST
shapiro.test(d) #p = 0.34
d <- B3D12$responseR1 - train$responseR2[train$blockNr == "Block3" & train$Trial == 16] #NOT NORM DIST
shapiro.test(d) #p = 0.23
d <- X3D12$responseR2 - train$responseR3[train$blockNr == "Block3" & train$Trial == 16] #NOT NORM DIST
shapiro.test(d) # 0.74
```

```{r}
#1) Are there significant differences between A, B and X when asked in their original block 1 and in the test phase
wilcox.test(A1D12$responseR1, train$responseR1[train$blockNr == "Block1" & train$Trial == 15], alternative = "two.sided", paired = T) #sign diff, decrease
wilcox.test(B1D12$responseR1, train$responseR2[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = T) #sign diff, increase
wilcox.test(X1D12$responseR2, train$responseR3[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = T) #no sign


#2) Are there sign differences between A, B and X when asked in block 3 and in the test phase
wilcox.test(A3D12$responseR1, train$responseR1[train$blockNr == "Block3" & train$Trial == 15], alternative = "two.sided", paired = T) #no diff
wilcox.test(B3D12$responseR1, train$responseR2[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff
wilcox.test(X3D12$responseR2, train$responseR3[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff (marg, increase)

```
```{r}
p <- c(0.0006951 , 0.0117, 0.1153, 0.2145, 0.6464, 0.06571)
p.adjust(p, method = "holm", n = length(p))
#yes, no (marg), no, no, no, no
```

```{r}
d <- CD12$responseR1 - A3D12$responseR1 
shapiro.test(d) # p = 0.04
d <- CD12$responseR1 - B3D12$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.07
d <- CD12$responseR1 - X3D12$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.27
 
d <- CD12$responseR1 - A1D12$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.32
d <- CD12$responseR1 - B1D12$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.34
d <- CD12$responseR1 - X1D12$responseR2 #NOT NORM DIST
shapiro.test(d) # 0.68
```

```{r}
#3) Is there a sign difference between the C value and that of A B and X in the test phase 
wilcox.test(CD12$responseR1, A3D12$responseR1, alternative = "two.sided", paired = T) #diff, lower C
wilcox.test(CD12$responseR1, B3D12$responseR1, alternative = "two.sided", paired = T) #no sign diff
wilcox.test(CD12$responseR1, X3D12$responseR2, alternative = "two.sided", paired = T) #diff, lower C


wilcox.test(CD12$responseR1, A1D12$responseR1, alternative = "two.sided", paired = T) #diff lower C
wilcox.test(CD12$responseR1, B1D12$responseR1, alternative = "two.sided", paired = T) #diff lower C
wilcox.test(CD12$responseR1, X1D12$responseR2, alternative = "two.sided", paired = T) #diff lower C
```
```{r}
p <- c(2.101e-06 , 0.1563, 0.0006998, 0.04826, 0.002248, 6.133e-05)
p.adjust(p, method = "holm", n = length(p))
#yes, no, yes,no,yes,yes
```


```{r}
d <- A1D12$responseR1 - A1F12$responseR1
shapiro.test(d) # p < 0.001
d <- B1D12$responseR1 - B1F12$responseR1
shapiro.test(d) #p < 0.001
d <- X1D12$responseR2 - X1F12$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.30
d<- CD12$responseR1 - CF12$responseR1
shapiro.test(d) # p = 0.002
d <- A3D12$responseR1 - A3F12$responseR1 
shapiro.test(d) #p < 0.001
d <- B3D12$responseR1 - B3F12$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.06
d <- X3D12$responseR2 - X3F12$responseR2
shapiro.test(d) #p < 0.001
```


```{r}
#4) Is there a difference between the ratings to fossil and those to diamond?
t.test(A1D12$responseR1, A1F12$responseR1, alternative = "two.sided", paired = T) #not sign
t.test(B1D12$responseR1, B1F12$responseR1, alternative = "two.sided", paired = T) #sign, fossil lower
t.test(X1D12$responseR2, X1F12$responseR2, alternative = "two.sided", paired = T) #sign, fossil lower
t.test(CD12$responseR1, CF12$responseR1, alternative = "two.sided", paired = T)   #no sign (makes sense! The cue is new)
t.test(A3D12$responseR1, A3F12$responseR1, alternative = "two.sided", paired = T) #sign, fossil lower
t.test(B3D12$responseR1, B3F12$responseR1, alternative = "two.sided", paired = T) #sign, fossil higher
t.test(X3D12$responseR2, X3F12$responseR2, alternative = "two.sided", paired = T) #not sign
```
```{r}
p <- c(0.1506, 0.003101, 0.00658, 0.3289, 2.805e-06, 0.01299, 0.183)
p.adjust(p, method = "holm", n = length(p))
#no, yes, yes, no, yes, no (marg), no
```

### Condition split

```{r}
#X000
X1F12000 <- testF12[which( (testF12$Trial == 2 | testF12$Trial == 4 | testF12$Trial == 6) & testF12$CondFirstBlock == "0") ,]
avgX1F12000 <- mean(X1F12000$responseR2, na.rm = T)
X1D12000 <- testD12[which( (testD12$Trial == 1 | testD12$Trial == 3 | testD12$Trial == 5) & testD12$CondFirstBlock == "0") ,]
avgX1D12000 <- mean(X1D12000$responseR2, na.rm = T)

X3F12000 <- testF12[which( (testF12$Trial == 8 | testF12$Trial == 10) & testF12$CondThirdBlock == "0"),]
avgX3F12000 <- mean(X3F12000$responseR2, na.rm = T)
X3D12000 <- testD12[which( (testD12$Trial == 7 | testD12$Trial == 9) & testD12$CondThirdBlock == "0"),]
avgX3D12000 <- mean(X3D12000$responseR2, na.rm = T)

#X050
X1F12050 <- testF12[which( (testF12$Trial == 2 | testF12$Trial == 4 | testF12$Trial == 6) & testF12$CondFirstBlock == "50") ,]
avgX1F12050 <- mean(X1F12050$responseR2, na.rm = T)
X1D12050 <- testD12[which( (testD12$Trial == 1 | testD12$Trial == 3 | testD12$Trial == 5) & testD12$CondFirstBlock == "50") ,]
avgX1D12050 <- mean(X1D12050$responseR2, na.rm = T)

X3F12050 <- testF12[which( (testF12$Trial == 8 | testF12$Trial == 10) & testF12$CondThirdBlock == "50"),]
avgX3F12050 <- mean(X3F12050$responseR2, na.rm = T)
X3D12050 <- testD12[which( (testD12$Trial == 7 | testD12$Trial == 9) & testD12$CondThirdBlock == "50"),]
avgX3D12050 <- mean(X3D12050$responseR2, na.rm = T)

#X100
X1F12100 <- testF12[which( (testF12$Trial == 2 | testF12$Trial == 4 | testF12$Trial == 6) & testF12$CondFirstBlock == "100") ,]
avgX1F12100 <- mean(X1F12100$responseR2, na.rm = T)
X1D12100 <- testD12[which( (testD12$Trial == 1 | testD12$Trial == 3 | testD12$Trial == 5) & testD12$CondFirstBlock == "100") ,]
avgX1D12100 <- mean(X1D12100$responseR2, na.rm = T)

X3F12100 <- testF12[which( (testF12$Trial == 8 | testF12$Trial == 10) & testF12$CondThirdBlock == "100"),]
avgX3F12100 <- mean(X3F12100$responseR2, na.rm = T)
X3D12100 <- testD12[which( (testD12$Trial == 7 | testD12$Trial == 9) & testD12$CondThirdBlock == "100"),]
avgX3D12100 <- mean(X3D12100$responseR2, na.rm = T)

#######################################
#A000
A1F12000 <- testF12[which( (testF12$Trial == 2 ) & testF12$CondFirstBlock == "0") ,]
avgA1F12000 <- mean(A1F12000$responseR1, na.rm = T)
A1D12000 <- testD12[which( (testD12$Trial == 1) & testD12$CondFirstBlock == "0") ,]
avgA1D12000 <- mean(A1D12000$responseR1, na.rm = T)

A3F12000 <- testF12[which( (testF12$Trial == 8) & testF12$CondThirdBlock == "0"),]
avgA3F12000 <- mean(A3F12000$responseR1, na.rm = T)
A3D12000 <- testD12[which( (testD12$Trial == 7) & testD12$CondThirdBlock == "0"),]
avgA3D12000 <- mean(A3D12000$responseR1, na.rm = T)

#A050
A1F12050 <- testF12[which( (testF12$Trial == 2) & testF12$CondFirstBlock == "50") ,]
avgA1F12050 <- mean(A1F12050$responseR1, na.rm = T)
A1D12050 <- testD12[which( (testD12$Trial == 1) & testD12$CondFirstBlock == "50") ,]
avgA1D12050 <- mean(A1D12050$responseR1, na.rm = T)

A3F12050 <- testF12[which( (testF12$Trial == 8) & testF12$CondThirdBlock == "50"),]
avgA3F12050 <- mean(A3F12050$responseR1, na.rm = T)
A3D12050 <- testD12[which( (testD12$Trial == 7) & testD12$CondThirdBlock == "50"),]
avgA3D12050 <- mean(A3D12050$responseR1, na.rm = T)

#A100
A1F12100 <- testF12[which( (testF12$Trial == 2) & testF12$CondFirstBlock == "100") ,]
avgA1F12100 <- mean(A1F12100$responseR1, na.rm = T)
A1D12100 <- testD12[which( (testD12$Trial == 1) & testD12$CondFirstBlock == "100") ,]
avgA1D12100 <- mean(A1D12100$responseR1, na.rm = T)

A3F12100 <- testF12[which( (testF12$Trial == 8) & testF12$CondThirdBlock == "100"),]
avgA3F12100 <- mean(A3F12100$responseR1, na.rm = T)
A3D12100 <- testD12[which( (testD12$Trial == 7) & testD12$CondThirdBlock == "100"),]
avgA3D12100 <- mean(A3D12100$responseR1, na.rm = T)

#######################################

#B000
B1F12000 <- testF12[which( (testF12$Trial == 4) & testF12$CondFirstBlock == "0") ,]
avgB1F12000 <- mean(B1F12000$responseR1, na.rm = T)
B1D12000 <- testD12[which( (testD12$Trial == 3) & testD12$CondFirstBlock == "0") ,]
avgB1D12000 <- mean(B1D12000$responseR1, na.rm = T)

B3F12000 <- testF12[which( (testF12$Trial == 10) & testF12$CondThirdBlock == "0"),]
avgB3F12000 <- mean(B3F12000$responseR1, na.rm = T)
B3D12000 <- testD12[which( (testD12$Trial == 9) & testD12$CondThirdBlock == "0"),]
avgB3D12000 <- mean(B3D12000$responseR1, na.rm = T)

#B050
B1F12050 <- testF12[which( (testF12$Trial == 4) & testF12$CondFirstBlock == "50") ,]
avgB1F12050 <- mean(B1F12050$responseR1, na.rm = T)
B1D12050 <- testD12[which( (testD12$Trial == 3) & testD12$CondFirstBlock == "50") ,]
avgB1D12050 <- mean(B1D12050$responseR1, na.rm = T)

B3F12050 <- testF12[which( (testF12$Trial == 10) & testF12$CondThirdBlock == "50"),]
avgB3F12050 <- mean(B3F12050$responseR1, na.rm = T)
B3D12050 <- testD12[which( (testD12$Trial == 9) & testD12$CondThirdBlock == "50"),]
avgB3D12050 <- mean(B3D12050$responseR1, na.rm = T)

#B100
B1F12100 <- testF12[which( (testF12$Trial == 4) & testF12$CondFirstBlock == "100") ,]
avgB1F12100 <- mean(B1F12100$responseR1, na.rm = T)
B1D12100 <- testD12[which( (testD12$Trial == 3) & testD12$CondFirstBlock == "100") ,]
avgB1D12100 <- mean(B1D12100$responseR1, na.rm = T)

B3F12100 <- testF12[which( (testF12$Trial == 10) & testF12$CondThirdBlock == "100"),]
avgB3F12100 <- mean(B3F12100$responseR1, na.rm = T)
B3D12100 <- testD12[which( (testD12$Trial == 9) & testD12$CondThirdBlock == "100"),]
avgB3D12100 <- mean(B3D12100$responseR1, na.rm = T)


#as C was never askeD12 beF12ore we cannot really compare it over conD12itions
#C
CF12 <- testF12[which(testF12$Trial == 6),]
avgCF12 <- mean(CF12$responseR1, na.rm = T)
CD12 <- testD12[which(testD12$Trial == 5),]
avgCD12 <- mean(CD12$responseR1, na.rm = T)


Cue <- c("A1","A1","A1", "B1", "B1", "B1", "X1", "X1", "X1", "C", "A3", "A3", "A3", "B3", "B3", "B3", "X3", "X3", "X3")
Cond <- c("0", "50", "100", "0", "50", "100", "0", "50", "100", "NA", "0", "50", "100", "0", "50", "100", "0", "50", "100")
Diamond <- c(avgA1D12000, avgA1D12050, avgA1D12100, avgB1D12000, avgB1D12050, avgB1D12100, avgX1D12000, avgX1D12050, avgX1D12100, avgCD12, avgA3D12000, avgA3D12050, avgA3D12100, avgB3D12000, avgB3D12050, avgB3D12100, avgX3D12000, avgX3D12050, avgX3D12100)
Fossil <- c(avgA1F12000, avgA1F12050, avgA1F12100, avgB1F12000, avgB1F12050, avgB1F12100, avgX1F12000, avgX1F12050, avgX1F12100, avgCF12, avgA3F12000, avgA3F12050, avgA3F12100, avgB3F12000, avgB3F12050, avgB3F12100, avgX3F12000, avgX3F12050, avgX3F12100)
Phase1Split <- data.frame(Cue, Cond, Diamond, Fossil)
Phase1Split
```

```{r}
#and now to add on to that, the original ones

#now that we know what was asked when in the training phase 
#we only take the last response just as before
ABl1000 <- mean(train$responseR1[train$blockNr == "Block1" & train$Cond == "0" & train$Trial == 15], na.rm = T)
ABl1050 <- mean(train$responseR1[train$blockNr == "Block1" & train$Cond == "50" & train$Trial == 15], na.rm = T)
ABl1100 <- mean(train$responseR1[train$blockNr == "Block1" & train$Cond == "100" & train$Trial == 15], na.rm = T)

BBl1000 <- mean(train$responseR2[train$blockNr == "Block1" & train$Cond == "0" & train$Trial == 16], na.rm = T)
BBl1050 <- mean(train$responseR2[train$blockNr == "Block1" & train$Cond == "50" & train$Trial == 16], na.rm = T)
BBl1100 <- mean(train$responseR2[train$blockNr == "Block1" & train$Cond == "100" & train$Trial == 16], na.rm = T)

XBl1000 <- mean(train$responseR3[train$blockNr == "Block1" & train$Cond == "0" & train$Trial == 16], na.rm = T)
XBl1050 <- mean(train$responseR3[train$blockNr == "Block1" & train$Cond == "50" & train$Trial == 16], na.rm = T)
XBl1100 <- mean(train$responseR3[train$blockNr == "Block1" & train$Cond == "100" & train$Trial == 16], na.rm = T)

ABl3000 <- mean(train$responseR1[train$blockNr == "Block3" & train$Cond == "0" & train$Trial == 15], na.rm = T)
ABl3050 <- mean(train$responseR1[train$blockNr == "Block3" & train$Cond == "50" & train$Trial == 15], na.rm = T)
ABl3100 <- mean(train$responseR1[train$blockNr == "Block3" & train$Cond == "100" & train$Trial == 15], na.rm = T)

BBl3000 <- mean(train$responseR2[train$blockNr == "Block3" & train$Cond == "0" & train$Trial == 16], na.rm = T)
BBl3050 <- mean(train$responseR2[train$blockNr == "Block3" & train$Cond == "50" & train$Trial == 16], na.rm = T)
BBl3100 <- mean(train$responseR2[train$blockNr == "Block3" & train$Cond == "100" & train$Trial == 16], na.rm = T)

XBl3000 <- mean(train$responseR3[train$blockNr == "Block3" & train$Cond == "0"& train$Trial == 16], na.rm = T)
XBl3050 <- mean(train$responseR3[train$blockNr == "Block3" & train$Cond == "50"& train$Trial == 16], na.rm = T)
XBl3100 <- mean(train$responseR3[train$blockNr == "Block3" & train$Cond == "100"& train$Trial == 16], na.rm = T)

Original <- c(ABl1000, ABl1050, ABl1100, BBl1000, BBl1050, BBl1100, XBl1000, XBl1050, XBl1100, "NA", ABl3000, ABl3050, ABl3100, BBl3000, BBl3050, BBl3100, XBl3000, XBl3050, XBl3100)
Phase1Split$Original <- as.numeric(Original)
Phase1Split
```

```{r}
A1D12000 <- aggregate(list(A1D12000$responseR1), by = list(A1D12000$prolific_id), mean, na.rm = T)
names(A1D12000) <- c("Participant", "responseR1")
A1D12050 <- aggregate(list(A1D12050$responseR1), by = list(A1D12050$prolific_id), mean, na.rm = T)
names(A1D12050) <- c("Participant", "responseR1")
A1D12100 <- aggregate(list(A1D12100$responseR1), by = list(A1D12100$prolific_id), mean, na.rm = T)
names(A1D12100) <- c("Participant", "responseR1")

B1D12000 <- aggregate(list(B1D12000$responseR1), by = list(B1D12000$prolific_id), mean, na.rm = T)
names(B1D12000) <- c("Participant", "responseR1")
B1D12050 <- aggregate(list(B1D12050$responseR1), by = list(B1D12050$prolific_id), mean, na.rm = T)
names(B1D12050) <- c("Participant", "responseR1")
B1D12100 <- aggregate(list(B1D12100$responseR1), by = list(B1D12100$prolific_id), mean, na.rm = T)
names(B1D12100) <- c("Participant", "responseR1")


X1D12000 <- aggregate(list(X1D12000$responseR2), by = list(X1D12000$prolific_id), mean, na.rm = T)
names(X1D12000) <- c("Participant", "responseR2")
X1D12050 <- aggregate(list(X1D12050$responseR2), by = list(X1D12050$prolific_id), mean, na.rm = T)
names(X1D12050) <- c("Participant", "responseR2")
X1D12100 <- aggregate(list(X1D12100$responseR2), by = list(X1D12100$prolific_id), mean, na.rm = T)
names(X1D12100) <- c("Participant", "responseR2")

A3D12000 <- aggregate(list(A3D12000$responseR1), by = list(A3D12000$prolific_id), mean, na.rm = T)
names(A3D12000) <- c("Participant", "responseR1")
A3D12050 <- aggregate(list(A3D12050$responseR1), by = list(A3D12050$prolific_id), mean, na.rm = T)
names(A3D12050) <- c("Participant", "responseR1")
A3D12100 <- aggregate(list(A3D12100$responseR1), by = list(A3D12100$prolific_id), mean, na.rm = T)
names(A3D12100) <- c("Participant", "responseR1")

B3D12000 <- aggregate(list(B3D12000$responseR1), by = list(B3D12000$prolific_id), mean, na.rm = T)
names(B3D12000) <- c("Participant", "responseR1")
B3D12050 <- aggregate(list(B3D12050$responseR1), by = list(B3D12050$prolific_id), mean, na.rm = T)
names(B3D12050) <- c("Participant", "responseR1")
B3D12100 <- aggregate(list(B3D12100$responseR1), by = list(B3D12100$prolific_id), mean, na.rm = T)
names(B3D12100) <- c("Participant", "responseR1")


X3D12000 <- aggregate(list(X3D12000$responseR2), by = list(X3D12000$prolific_id), mean, na.rm = T)
names(X3D12000) <- c("Participant", "responseR2")
X3D12050 <- aggregate(list(X3D12050$responseR2), by = list(X3D12050$prolific_id), mean, na.rm = T)
names(X3D12050) <- c("Participant", "responseR2")
X3D12100 <- aggregate(list(X3D12100$responseR2), by = list(X3D12100$prolific_id), mean, na.rm = T)
names(X3D12100) <- c("Participant", "responseR2")


A1F12000 <- aggregate(list(A1F12000$responseR1), by = list(A1F12000$prolific_id), mean, na.rm = T)
names(A1F12000) <- c("Participant", "responseR1")
A1F12050 <- aggregate(list(A1F12050$responseR1), by = list(A1F12050$prolific_id), mean, na.rm = T)
names(A1F12050) <- c("Participant", "responseR1")
A1F12100 <- aggregate(list(A1F12100$responseR1), by = list(A1F12100$prolific_id), mean, na.rm = T)
names(A1F12100) <- c("Participant", "responseR1")

B1F12000 <- aggregate(list(B1F12000$responseR1), by = list(B1F12000$prolific_id), mean, na.rm = T)
names(B1F12000) <- c("Participant", "responseR1")
B1F12050 <- aggregate(list(B1F12050$responseR1), by = list(B1F12050$prolific_id), mean, na.rm = T)
names(B1F12050) <- c("Participant", "responseR1")
B1F12100 <- aggregate(list(B1F12100$responseR1), by = list(B1F12100$prolific_id), mean, na.rm = T)
names(B1F12100) <- c("Participant", "responseR1")

X1F12000 <- aggregate(list(X1F12000$responseR2), by = list(X1F12000$prolific_id), mean, na.rm = T)
names(X1F12000) <- c("Participant", "responseR2")
X1F12050 <- aggregate(list(X1F12050$responseR2), by = list(X1F12050$prolific_id), mean, na.rm = T)
names(X1F12050) <- c("Participant", "responseR2")
X1F12100 <- aggregate(list(X1F12100$responseR2), by = list(X1F12100$prolific_id), mean, na.rm = T)
names(X1F12100) <- c("Participant", "responseR2")

A3F12000 <- aggregate(list(A3F12000$responseR1), by = list(A3F12000$prolific_id), mean, na.rm = T)
names(A3F12000) <- c("Participant", "responseR1")
A3F12050 <- aggregate(list(A3F12050$responseR1), by = list(A3F12050$prolific_id), mean, na.rm = T)
names(A3F12050) <- c("Participant", "responseR1")
A3F12100 <- aggregate(list(A3F12100$responseR1), by = list(A3F12100$prolific_id), mean, na.rm = T)
names(A3F12100) <- c("Participant", "responseR1")

B3F12000 <- aggregate(list(B3F12000$responseR1), by = list(B3F12000$prolific_id), mean, na.rm = T)
names(B3F12000) <- c("Participant", "responseR1")
B3F12050 <- aggregate(list(B3F12050$responseR1), by = list(B3F12050$prolific_id), mean, na.rm = T)
names(B3F12050) <- c("Participant", "responseR1")
B3F12100 <- aggregate(list(B3F12100$responseR1), by = list(B3F12100$prolific_id), mean, na.rm = T)
names(B3F12100) <- c("Participant", "responseR1")


X3F12000 <- aggregate(list(X3F12000$responseR2), by = list(X3F12000$prolific_id), mean, na.rm = T)
names(X3F12000) <- c("Participant", "responseR2")
X3F12050 <- aggregate(list(X3F12050$responseR2), by = list(X3F12050$prolific_id), mean, na.rm = T)
names(X3F12050) <- c("Participant", "responseR2")
X3F12100 <- aggregate(list(X3F12100$responseR2), by = list(X3F12100$prolific_id), mean, na.rm = T)
names(X3F12100) <- c("Participant", "responseR2")
```


### Differences between scoring per cond?
```{r}
d <- A1D12000$responseR1 - A1D12050$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.28
d <- A1D12050$responseR1 - A1D12100$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.97
d <- A1D12100$responseR1 - A1D12000$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.74

d <- B1D12000$responseR1 - B1D12050$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.93
d <- B1D12050$responseR1 - B1D12100$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.34
d <- B1D12100$responseR1 - B1D12000$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.08

d <- X1D12000$responseR2 - X1D12050$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.53
d <- X1D12050$responseR2 - X1D12100$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.27
d <- X1D12100$responseR2 - X1D12000$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.35

d <- A3D12000$responseR1 - A3D12050$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.15
d <- A3D12050$responseR1 - A3D12100$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.33
d <- A3D12100$responseR1 - A3D12000$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.46

d <- B3D12000$responseR1 - B3D12050$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.61
d <- B3D12050$responseR1 - B3D12100$responseR1
shapiro.test(d) #p = 0.01
d <- B3D12100$responseR1 - B3D12000$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.61

d <- X3D12000$responseR2 - X3D12050$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.74
d <- X3D12050$responseR2 - X3D12100$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.67
d <- X3D12100$responseR2 - X3D12000$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.85


```

<br/> Now we no longer have the same group of people (some did 50-50 in their first block, but they were not the same as the people that did 75-25 in their first block), so here it's unpaired data!
```{r}
wilcox.test(A1D12000$responseR1, A1D12050$responseR1, alternative = "two.sided", paired = F) #no diff 
wilcox.test(A1D12050$responseR1, A1D12100$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(A1D12100$responseR1, A1D12000$responseR1, alternative = "two.sided", paired = F) #no diff

wilcox.test(B1D12000$responseR1, B1D12050$responseR1, alternative = "two.sided", paired = F) #no diff 
wilcox.test(B1D12050$responseR1, B1D12100$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(B1D12100$responseR1, B1D12000$responseR1, alternative = "two.sided", paired = F) #no diff

wilcox.test(X1D12000$responseR2, X1D12050$responseR2, alternative = "two.sided", paired = F) #no diff 
wilcox.test(X1D12050$responseR2, X1D12100$responseR2, alternative = "two.sided", paired = F) #no diff
wilcox.test(X1D12100$responseR2, X1D12000$responseR2, alternative = "two.sided", paired = F) #no diff
```

```{r}
wilcox.test(A3D12000$responseR1, A3D12050$responseR1, alternative = "two.sided", paired = F) #no diff 
wilcox.test(A3D12050$responseR1, A3D12100$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(A3D12100$responseR1, A3D12000$responseR1, alternative = "two.sided", paired = F) #no diff

wilcox.test(B3D12000$responseR1, B3D12050$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(B3D12050$responseR1, B3D12100$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(B3D12100$responseR1, B3D12000$responseR1, alternative = "two.sided", paired = F) #no diff

wilcox.test(X3D12000$responseR2, X3D12050$responseR2, alternative = "two.sided", paired = F) #no diff 
wilcox.test(X3D12050$responseR2, X3D12100$responseR2, alternative = "two.sided", paired = F) #no diff
wilcox.test(X3D12100$responseR2, X3D12000$responseR2, alternative = "two.sided", paired = F) #no diff
```

```{r}
p <- c(0.479,0.6912,0.7235,0.3573,0.3964,0.8694,0.3975,0.9662,0.3711,0.5983,0.5254,0.3284, 0.2091, 0.5873, 0.4108, 0.4497, 0.6322,0.5724)
p.adjust(p, method = "holm", n = length(p))
#all 1's, so all no
```

####  Difference training and test phase

```{r}
d <- A1D12000$responseR1 - (train$responseR1[train$Cond == "0" & train$Trial == 15 & train$blockNr == "Block1"]) #NOT NORM DIST
shapiro.test(d) # p = 0.71
d <- A1D12050$responseR1 - (train$responseR1[train$Cond == "50" & train$Trial == 15 & train$blockNr == "Block1"]) #NOT NORM DIST
shapiro.test(d) # p = 0.33
d <- A1D12100$responseR1 - (train$responseR1[train$Cond == "100" & train$Trial == 15 & train$blockNr == "Block1"]) #NOT NORM DIST
shapiro.test(d) # p = 0.49

d <- B1D12000$responseR1 - (train$responseR2[train$Cond == "0" & train$Trial == 16 & train$blockNr == "Block1"])
shapiro.test(d) # p = 0.03
d <- B1D12050$responseR1 - (train$responseR2[train$Cond == "50" & train$Trial == 16 & train$blockNr == "Block1"]) #NOT NORM DIST
shapiro.test(d) # p = 0.45
d <- B1D12100$responseR1 - (train$responseR2[train$Cond == "100" & train$Trial == 16 & train$blockNr == "Block1"]) #NOT NORM DIST
shapiro.test(d) # p = 0.88

d <- X1D12000$responseR2 - (train$responseR3[train$Cond == "0" & train$Trial == 16 & train$blockNr == "Block1"]) #NOT NORM DIST
shapiro.test(d) # p = 0.33
d <- X1D12050$responseR2 - (train$responseR3[train$Cond == "50" & train$Trial == 16 & train$blockNr == "Block1"]) #NOT NORM DIST
shapiro.test(d) # p = 0.21
d <- X1D12100$responseR2 - (train$responseR3[train$Cond == "100" & train$Trial == 16 & train$blockNr == "Block1"]) #NOT NORM DIST
shapiro.test(d) # p = 0.96

d <- A3D12000$responseR1 - (train$responseR1[train$Cond == "0" & train$Trial == 15 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.33
d <- A3D12050$responseR1 - (train$responseR1[train$Cond == "50" & train$Trial == 15 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.21
d <- A3D12100$responseR1 - (train$responseR1[train$Cond == "100" & train$Trial == 15 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.70

d <- B3D12000$responseR1 - (train$responseR2[train$Cond == "0" & train$Trial == 16 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.41
d <- B3D12050$responseR1 - (train$responseR2[train$Cond == "50" & train$Trial == 16 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.93
d <- B3D12100$responseR1 - (train$responseR2[train$Cond == "100" & train$Trial == 16 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.69

d <- X3D12000$responseR2 - (train$responseR3[train$Cond == "0" & train$Trial == 16 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.44
d <- X3D12050$responseR2 - (train$responseR3[train$Cond == "50" & train$Trial == 16 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.39
d <- X3D12100$responseR2 - (train$responseR3[train$Cond == "100" & train$Trial == 16 & train$blockNr == "Block3"]) #NOT NORM DIST
shapiro.test(d) # p = 0.56
```

<br/> here we do have similar participants, so now it's pared again
```{r}
#1) Are there significant differences between A, B and X when asked in their original block 1 and in the test phase
wilcox.test(A1D12000$responseR1, (train$responseR1[train$Cond == "0" & train$Trial == 15 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(A1D12050$responseR1, (train$responseR1[train$Cond == "50" & train$Trial == 15 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #sign diff, training HIGHER than test
wilcox.test(A1D12100$responseR1, (train$responseR1[train$Cond == "100" & train$Trial == 15 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #sign diff, training HIGHER than test

wilcox.test(B1D12000$responseR1, (train$responseR2[train$Cond == "0" & train$Trial == 16 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(B1D12050$responseR1, (train$responseR2[train$Cond == "50" & train$Trial == 16 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(B1D12100$responseR1, (train$responseR2[train$Cond == "100" & train$Trial == 16 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #dif, test higher than train

wilcox.test(X1D12000$responseR2, (train$responseR3[train$Cond == "0" & train$Trial == 16 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(X1D12050$responseR2, (train$responseR3[train$Cond == "50" & train$Trial == 16 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(X1D12100$responseR2, (train$responseR3[train$Cond == "100" & train$Trial == 16 & train$blockNr == "Block1"]), alternative = "two.sided", paired = T) #no diff

#2) Are there sign differences between A, B and X when asked in block 3 and in the test phase
wilcox.test(A3D12000$responseR1, (train$responseR1[train$Cond == "0" & train$Trial == 15 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(A3D12050$responseR1, (train$responseR1[train$Cond == "50" & train$Trial == 15 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(A3D12100$responseR1, (train$responseR1[train$Cond == "100" & train$Trial == 15 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #no diff 

wilcox.test(B3D12000$responseR1, (train$responseR2[train$Cond == "0" & train$Trial == 16 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(B3D12050$responseR1, (train$responseR2[train$Cond == "50" & train$Trial == 16 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(B3D12100$responseR1, (train$responseR2[train$Cond == "100" & train$Trial == 16 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #no diff

wilcox.test(X3D12000$responseR2, (train$responseR3[train$Cond == "0" & train$Trial == 16 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(X3D12050$responseR2, (train$responseR3[train$Cond == "50" & train$Trial == 16 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #no diff
wilcox.test(X3D12100$responseR2, (train$responseR3[train$Cond == "100" & train$Trial == 16 & train$blockNr == "Block3"]), alternative = "two.sided", paired = T) #diff test higher than train

```
```{r}
p <- c(0.5186,0.0175,0.02144,0.6253,0.3816,0.01198,0.3801,0.306,0.235,0.09324,0.321, 0.4003, 0.1158, 0.4769, 0.3203, 0.6888,0.7363,0.01204 )
p.adjust(p, method = "holm", n = length(p))
#All no
```


```{r}
d <- CD12$responseR1 - A1D12000$responseR1
shapiro.test(d) #p = 0.04
d <- CD12$responseR1 - A1D12050$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.15
d <- CD12$responseR1 - A1D12100$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.07

d <- CD12$responseR1 - B1D12000$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.28
d <- CD12$responseR1 - B1D12050$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.28
d <- CD12$responseR1 - B1D12100$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.09

d <- CD12$responseR1 - X1D12000$responseR2
shapiro.test(d) #p = 0.03
d <- CD12$responseR1 - X1D12050$responseR2
shapiro.test(d) #p = 0.02
d <- CD12$responseR1 - X1D12100$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.10

d <- CD12$responseR1 - A3D12000$responseR1
shapiro.test(d) #p < 0.001
d <- CD12$responseR1 - A3D12050$responseR1
shapiro.test(d) #p = 0.001
d <- CD12$responseR1 - A3D12100$responseR1
shapiro.test(d) #p = 0.001

d <- CD12$responseR1 - B3D12000$responseR1
shapiro.test(d) #p = 0.007
d <- CD12$responseR1 - B3D12050$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.25
d <- CD12$responseR1 - B3D12100$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.23

d <- CD12$responseR1 - X3D12000$responseR2
shapiro.test(d) #p = 0.006
d <- CD12$responseR1 - X3D12050$responseR2 #NOT NORM DIST
shapiro.test(d) #p = 0.09
d <- CD12$responseR1 - X3D12100$responseR2
shapiro.test(d) #p = 0.03

```

<br/> uuh normally my strategy is hey choose the one that is most frequent, but this is literally 50/50?
<br/> unpaired here because C is not dependend on what the block of the first or third cue was. So while everyone that saw A1D12000 saw C, not everyone that saw C saw 50-50 as their first condition. 
#### This is def the one I'm most unsure about
```{r}
#3) Is there a sign difference between the C value and that of A B and X in the test phase 
wilcox.test(CD12$responseR1, A1D12000$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(CD12$responseR1, A1D12050$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(CD12$responseR1, A1D12100$responseR1, alternative = "two.sided", paired = F) #no diff

wilcox.test(CD12$responseR1, B1D12000$responseR1, alternative = "two.sided", paired = F) #diff, c lower
wilcox.test(CD12$responseR1, B1D12050$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(CD12$responseR1, B1D12100$responseR1, alternative = "two.sided", paired = F) #diff, C lower

wilcox.test(CD12$responseR1, X1D12000$responseR2, alternative = "two.sided", paired = F) #diff, C lower
wilcox.test(CD12$responseR1, X1D12050$responseR2, alternative = "two.sided", paired = F) #diff, C lower
wilcox.test(CD12$responseR1, X1D12100$responseR2, alternative = "two.sided", paired = F) #diff, C lower

wilcox.test(CD12$responseR1, A3D12000$responseR1, alternative = "two.sided", paired = F) #diff, C lower
wilcox.test(CD12$responseR1, A3D12050$responseR1, alternative = "two.sided", paired = F) #diff, C lower
wilcox.test(CD12$responseR1, A3D12100$responseR1, alternative = "two.sided", paired = F) #diff, C lower

wilcox.test(CD12$responseR1, B3D12000$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(CD12$responseR1, B3D12050$responseR1, alternative = "two.sided", paired = F) #no diff
wilcox.test(CD12$responseR1, B3D12100$responseR1, alternative = "two.sided", paired = F) #no diff

wilcox.test(CD12$responseR1, X3D12000$responseR2, alternative = "two.sided", paired = F) #no diff
wilcox.test(CD12$responseR1, X3D12050$responseR2, alternative = "two.sided", paired = F) #diff, C lower
wilcox.test(CD12$responseR1, X3D12100$responseR2, alternative = "two.sided", paired = F) #diff, C lower
```
```{r}
p <- c(0.04678,0.242,0.06531,0.008871,0.1041,0.01075,0.0001978,0.005238,0.001063,3.846e-05,0.0001376, 0.0003143, 0.1754, 0.9002, 0.4739,  0.1004,0.002267,0.001723 )
p.adjust(p, method = "holm", n = length(p))
#no,no,no no,no,no yes,no(marg),yes, yes,yes,yes, no,no,no no,yes,yes)
```



```{r}
d <- A1D12000$responseR1 - A1F12000$responseR1 
shapiro.test(d)# p = 0.003
d <- A1D12050$responseR1 - A1F12050$responseR1 #NOT NORM DIST 
shapiro.test(d)# p = 0.17
d <- A1D12100$responseR1 - A1F12100$responseR1 #NOT NORM DIST  
shapiro.test(d)# p = 0.056

d <- B1D12000$responseR1 - B1F12000$responseR1 
shapiro.test(d)# p = 0.007
d <- B1D12050$responseR1 - B1F12050$responseR1 
shapiro.test(d)# p = 0.01
d <- B1D12100$responseR1 - B1F12100$responseR1 #NOT NORM DIST  
shapiro.test(d)# p = 0.08

d <- X1D12000$responseR2 - X1F12000$responseR2 #NOT NORM DIST 
shapiro.test(d)# p = 0.16
d <- X1D12050$responseR2 - X1F12050$responseR2 #NOT NORM DIST  
shapiro.test(d)# p = 0.98
d <- X1D12100$responseR2 - X1F12100$responseR2 #NOT NORM DIST  
shapiro.test(d)# p = 0.25

d <- A3D12000$responseR1 - A3F12000$responseR1 #NOT NORM DIST  
shapiro.test(d)# p = 0.12
d <- A3D12050$responseR1 - A3F12050$responseR1 #NOT NORM DIST  
shapiro.test(d)# p = 0.09
d <- A3D12100$responseR1 - A3F12100$responseR1 
shapiro.test(d)# p = 0.03

d <- B3D12000$responseR1 - B3F12000$responseR1 #NOT NORM DIST  
shapiro.test(d)# p = 0.38
d <- B3D12050$responseR1 - B3F12050$responseR1 #NOT NORM DIST  
shapiro.test(d)# p = 0.21
d <- B3D12100$responseR1 - B3F12100$responseR1 
shapiro.test(d)# p = 0.03

d <- X3D12000$responseR2 - X3F12000$responseR2 
shapiro.test(d)# p = 0.02
d <- X3D12050$responseR2 - X3F12050$responseR2 #NOT NORM DIST  
shapiro.test(d)# p = 0.45
d <- X3D12100$responseR2 - X3F12100$responseR2 
shapiro.test(d)# p < 0.001
```

```{r}
#4) Is there a difference between the ratings to fossil and those to diamond?
wilcox.test(A1D12000$responseR1, A1F12000$responseR1, alternative = "two.sided", paired = T) #no diff
wilcox.test(A1D12050$responseR1, A1F12050$responseR1, alternative = "two.sided", paired = T) #no diff
wilcox.test(A1D12100$responseR1, A1F12100$responseR1, alternative = "two.sided", paired = T) #no diff

wilcox.test(B1D12000$responseR1, B1F12000$responseR1, alternative = "two.sided", paired = T) #diff, fossil lower
wilcox.test(B1D12050$responseR1, B1F12050$responseR1, alternative = "two.sided", paired = T) #no diff
wilcox.test(B1D12100$responseR1, B1F12100$responseR1, alternative = "two.sided", paired = T) #diff, fossil lower

wilcox.test(X1D12000$responseR2, X1F12000$responseR2, alternative = "two.sided", paired = T) #diff, fossil lower
wilcox.test(X1D12050$responseR2, X1F12050$responseR2, alternative = "two.sided", paired = T) #no diff
wilcox.test(X1D12100$responseR2, X1F12100$responseR2, alternative = "two.sided", paired = T) #no diff

wilcox.test(A3D12000$responseR1, A3F12000$responseR1, alternative = "two.sided", paired = T) #diff, fossil lower
wilcox.test(A3D12050$responseR1, A3F12050$responseR1, alternative = "two.sided", paired = T) #diff, fossil lower
wilcox.test(A3D12100$responseR1, A3F12100$responseR1, alternative = "two.sided", paired = T) #diff, fossil lower

wilcox.test(B3D12000$responseR1, B3F12000$responseR1, alternative = "two.sided", paired = T) #diff, fossil higher
wilcox.test(B3D12050$responseR1, B3F12050$responseR1, alternative = "two.sided", paired = T) #no diff
wilcox.test(B3D12100$responseR1, B3F12100$responseR1, alternative = "two.sided", paired = T) #no diff

wilcox.test(X3D12000$responseR2, X3F12000$responseR2, alternative = "two.sided", paired = T) #no diff
wilcox.test(X3D12050$responseR2, X3F12050$responseR2, alternative = "two.sided", paired = T) #diff, fossil lower
wilcox.test(X3D12100$responseR2, X3F12100$responseR2, alternative = "two.sided", paired = T) #diff, fossil lower
```

```{r}
p <- c(0.2042,0.6476,0.4911,  0.04352,0.5279,0.002791,   0.0419,0.7403,0.08925,  0.01277,0.02464, 0.01753,   0.006216, 0.4759, 0.3991,  0.9686,0.248,0.3441)
p.adjust(p, method = "holm", n = length(p))
#no,no,no no,no,no(marg) no,no,no no,no,no no,no,no, no,no,no
```

### Phase 3
<br/> This phase introduced alternative versions of the stimuli (e.g instead of a mouse now a hamster), and reintroduced the "no diamond" outcome again.
<br/>

We want to know several things. The first being: what the average scores of the alternatives are and compare those to average of the original blocks?
```{r}
#Phase 3
testF3 <- testP3[which(testP3$Outcome == "Fossil.png"),]
testD3 <- testP3[which(testP3$Outcome == "Diamond.png"),]
testN3 <- testP3[which(testP3$Outcome == "NoDiamond.png"),]
#We also look at the NoDiamond outcome here, as that one is asked again

#the trial order this time around is different.


#X
X1F3 <- testF3[which(testF3$Trial == 2 | testF3$Trial == 5 | testF3$Trial == 8),]
avgX1F3 <- mean(X1F3$responseR2, na.rm = T)
X1D3 <- testD3[which(testD3$Trial == 1 | testD3$Trial == 4 | testD3$Trial == 7),]
avgX1D3 <- mean(X1D3$responseR2, na.rm = T)
X1N3 <- testN3[which(testN3$Trial == 3 | testN3$Trial == 6 | testN3$Trial == 9),]
avgX1N3 <- mean(X1N3$responseR2, na.rm = T)
X3F3 <- testF3[which(testF3$Trial == 11 | testF3$Trial == 14),]
avgX3F3 <- mean(X3F3$responseR2, na.rm = T)
X3D3 <- testD3[which(testD3$Trial == 10 | testD3$Trial == 13),]
avgX3D3 <- mean(X3D3$responseR2, na.rm = T)
X3N3 <- testN3[which(testN3$Trial == 12 | testN3$Trial == 15),]
avgX3N3 <- mean(X3N3$responseR2, na.rm = T)


#A
A1F3 <- testF3[which(testF3$Trial == 2),]
avgA1F3 <- mean(A1F3$responseR1, na.rm = T)
A1D3 <- testD3[which(testD3$Trial == 1),]
avgA1D3 <- mean(A1D3$responseR1, na.rm = T)
A1N3 <- testN3[which(testN3$Trial == 3),]
avgA1N3 <- mean(A1N3$responseR1, na.rm = T)
A3F3 <- testF3[which(testF3$Trial == 11),]
avgA3F3 <- mean(A3F3$responseR1, na.rm = T)
A3D3 <- testD3[which(testD3$Trial == 10),]
avgA3D3 <- mean(A3D3$responseR1, na.rm = T)
A3N3 <- testN3[which(testN3$Trial == 12),]
avgA3N3 <- mean(A3N3$responseR1, na.rm = T)

#B
B1F3 <- testF3[which(testF3$Trial == 5),]
avgB1F3 <- mean(B1F3$responseR1, na.rm = T)
B1D3 <- testD3[which(testD3$Trial == 4),]
avgB1D3 <- mean(B1D3$responseR1, na.rm = T)
B1N3 <- testN3[which(testN3$Trial == 6),]
avgB1N3 <- mean(B1N3$responseR1, na.rm = T)
B3F3 <- testF3[which(testF3$Trial == 14),]
avgB3F3 <- mean(B3F3$responseR1, na.rm = T)
B3D3 <- testD3[which(testD3$Trial == 13),]
avgB3D3 <- mean(B3D3$responseR1, na.rm = T)
B3N3 <- testN3[which(testN3$Trial == 15),]
avgB3N3 <- mean(B3N3$responseR1, na.rm = T)

#C
CF3 <- testF3[which(testF3$Trial == 8),]
avgCF3 <- mean(CF3$responseR1, na.rm = T)
CD3 <- testD3[which(testD3$Trial == 7),]
avgCD3 <- mean(CD3$responseR1, na.rm = T)
CN3 <- testN3[which(testN3$Trial == 9),]
avgCN3 <- mean(CN3$responseR1, na.rm = T)

Diamond3 <- c(avgA1D3, avgB1D3, avgX1D3, avgCD3, avgA3D3, avgB3D3, avgX3D3)
Fossil3 <- c(avgA1F3, avgB1F3, avgX1F3, avgCF3, avgA3F3, avgB3F3, avgX3F3)
NoDiamond3 <- c(avgA1N3, avgB1N3, avgX1N3, avgCN3, avgA3N3, avgB3N3, avgX3N3)
Cue <- c("A1", "B1", "X1", "C", "A3", "B3", "X3")
Phase3 <- data.frame(Cue, Diamond3, Fossil3, NoDiamond3)

Original <- c(ABl1, BBl1, XBl1, "NA", ABl3, BBl3, XBl3)
Phase3$Original <- as.numeric(Original)
Phase3
```

```{r}
A1D3 <- aggregate(list(A1D3$responseR1), by = list(A1D3$prolific_id), mean, na.rm = T)
names(A1D3) <- c("Participant", "responseR1")
B1D3 <- aggregate(list(B1D3$responseR1), by = list(B1D3$prolific_id), mean, na.rm = T)
names(B1D3) <- c("Participant", "responseR1")
X1D3 <- aggregate(list(X1D3$responseR2), by = list(X1D3$prolific_id), mean, na.rm = T)
names(X1D3) <- c("Participant", "responseR2")

A3D3 <- aggregate(list(A3D3$responseR1), by = list(A3D3$prolific_id), mean, na.rm = T)
names(A3D3) <- c("Participant", "responseR1")
B3D3 <- aggregate(list(B3D3$responseR1), by = list(B3D3$prolific_id), mean, na.rm = T)
names(B3D3) <- c("Participant", "responseR1")
X3D3 <- aggregate(list(X3D3$responseR2), by = list(X3D3$prolific_id), mean, na.rm = T)
names(X3D3) <- c("Participant", "responseR2")

A1N3 <- aggregate(list(A1N3$responseR1), by = list(A1N3$prolific_id), mean, na.rm = T)
names(A1N3) <- c("Participant", "responseR1")
B1N3 <- aggregate(list(B1N3$responseR1), by = list(B1N3$prolific_id), mean, na.rm = T)
names(B1N3) <- c("Participant", "responseR1")
X1N3 <- aggregate(list(X1N3$responseR2), by = list(X1N3$prolific_id), mean, na.rm = T)
names(X1N3) <- c("Participant", "responseR2")

A3N3 <- aggregate(list(A3N3$responseR1), by = list(A3N3$prolific_id), mean, na.rm = T)
names(A3N3) <- c("Participant", "responseR1")
B3N3 <- aggregate(list(B3N3$responseR1), by = list(B3N3$prolific_id), mean, na.rm = T)
names(B3N3) <- c("Participant", "responseR1")
X3N3 <- aggregate(list(X3N3$responseR2), by = list(X3N3$prolific_id), mean, na.rm = T)
names(X3N3) <- c("Participant", "responseR2")

CD3 <- aggregate(list(CD3$responseR1), by = list(CD3$prolific_id), mean, na.rm =T)
names(CD3) <- c("Participant", "responseR1")
CN3 <- aggregate(list(CN3$responseR1), by = list(CN3$prolific_id), mean, na.rm =T)
names(CN3) <- c("Participant", "responseR1")
```

```{r}
d <- A1D3$responseR1 - train$responseR1[train$blockNr == "Block1" & train$Trial == 15]
shapiro.test(d) #p = 0.01
d <- B1D3$responseR1 - train$responseR2[train$blockNr == "Block1" & train$Trial == 16]
shapiro.test(d) #p = 0.03
d <- X1D3$responseR2 - train$responseR3[train$blockNr == "Block1" & train$Trial == 16] #NOT NORM DIST
shapiro.test(d) #p = 0.21

d <- A3D3$responseR1 - train$responseR1[train$blockNr == "Block3" & train$Trial == 15] #NOT NORM DIST
shapiro.test(d) #p = 0.06
d <- B3D3$responseR1 - train$responseR2[train$blockNr == "Block3" & train$Trial == 16] #NOT NORM DIST
shapiro.test(d) #p = 0.76
d <- X3D3$responseR2 - train$responseR3[train$blockNr == "Block3" & train$Trial == 16] #NOT NORM DIST
shapiro.test(d) #p = 0.45

```

```{r}
#differences to the original stimuli in the training phase
wilcox.test(A1D3$responseR1, train$responseR1[train$blockNr == "Block1" & train$Trial == 15], alternative = "two.sided", paired = T) #diff, train higher
wilcox.test(B1D3$responseR1, train$responseR2[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff
wilcox.test(X1D3$responseR2, train$responseR3[train$blockNr == "Block1" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff

wilcox.test(A3D3$responseR1, train$responseR1[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff
wilcox.test(B3D3$responseR1, train$responseR2[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff
wilcox.test(X3D3$responseR2, train$responseR3[train$blockNr == "Block3" & train$Trial == 16], alternative = "two.sided", paired = T) #no diff

#there are no significant differences between the scores to diamond in the test phase and the scores given in the original block.
#It seems then as though people did notice the categories (although I do have to see all the averages are around 4, so I wouldn't say that with certainty.)
```
```{r}
p <- c(0.004767,0.3799,0.388,  0.06809,0.1416,0.146)
p.adjust(p, method = "holm", n = length(p))
#yes,no,no,no,no,no
```

```{r}
d <- A1D3$responseR1 - A1N3$responseR1
shapiro.test(d) #p < 0.001
d <- B1D3$responseR1 - B1N3$responseR1
shapiro.test(d) #p = 0.01
d <- X1D3$responseR2 - X1N3$responseR2
shapiro.test(d) #p < 0.001

d <- A3D3$responseR1 - A3N3$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.07
d <- B3D3$responseR1 - B3N3$responseR1 #NOT NORM DIST
shapiro.test(d) #p = 0.06
d <- X3D3$responseR2 - X3N3$responseR2
shapiro.test(d) #p = 0.008

```

```{r}
#what happens if we see if there is a difference to the scores of A, B and X to allergic and those to no allergic?
t.test(A1D3$responseR1, A1N3$responseR1, alternative = "two.sided", paired = T) #no diff
t.test(B1D3$responseR1, B1N3$responseR1, alternative = "two.sided", paired = T) #no diff
t.test(X1D3$responseR2, X1N3$responseR2, alternative = "two.sided", paired = T) #no diff
t.test(A3D3$responseR1, A3N3$responseR1, alternative = "two.sided", paired = T) #no diff
t.test(B3D3$responseR1, B3N3$responseR1, alternative = "two.sided", paired = T) #no diff
t.test(X3D3$responseR2, X3N3$responseR2, alternative = "two.sided", paired = T) #no diff
#No differences here. That might indicate that people just were very not sure, as there isn't a clear higher score for a diamond outcome than a non diamond outcome
```

```{r}
p <- c(0.4995,0.8479,0.5119,  0.1976,0.9669,0.8823)
p.adjust(p, method = "holm", n = length(p))
#no,no,no,no,no,no
```
